---
title: "AoA prediction template"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(dplyr.summarise.inform = FALSE)

# load libraries
library(tidyverse)
library(glue)
library(wordbankr)
install.packages("remotes")
remotes::install_github("langcog/childesr")
library(childesr)
library(broom)
library(car)
#library(jglmm)
library(modelr)
library(ggrepel)
library(SnowballC)
library(cowplot)
library(Hmisc)
library(arm)

# load functions
walk(list.files("scripts", pattern = "*.R$", full.names = TRUE), source)
```

This template provides the structure for how to fit age of acquisition (AoA) prediction models, using data and scripts in this repository.

The general steps are:
- loading the provided CDI data and predictor data
- adding your predictor(s) to the provided predictor data
- using the functions in `scripts/prep_data.R` to prepare the data for modeling
- using the functions in `scripts/fit_models.R` to fit models and extract information from them


# Load Wordbank data

Loading cached Wordbank data for English:
```{r load_wordbank_eng}
eng_wb_data <- readRDS("data/wordbank/english_(american).rds")
eng_wb_data
```

Loading cached Wordbank data for multiple languages:
```{r loadwordbankxling}
target_langs <- c("Croatian", "Danish", "English (American)", "Norwegian", "Russian", "Turkish", "Spanish (Mexican)", "Italian", "Swedish",  "French (Quebecois)") 
#"French (French)" "English (Australian)", "German","English (British)",
#Portuguese (European) Spanish (European)" have NA in unilemmas 

wb_data <- map_df(target_langs, function(lang) {
  message(glue("Loading data for {lang}..."))
  norm_lang <- normalize_language(lang)
  readRDS(glue("data/wordbank/{norm_lang}.rds"))
})
wb_data
```

Creating saved Wordbank data for English:
```{r create_wordbank_eng, eval=FALSE}
create_wb_data("Portuguese (European)")
```

Creating saved Wordbank data for many languages:
```{r create_wordbank_xling, eval=FALSE}
walk(target_langs, create_wb_data)
```

Creating saved Wordbank data one step at a time (potentially making changes between steps):
```{r create_wordbank_eng_steps, eval=FALSE}
eng_wg <- create_inst_data("English (American)", "WG")
eng_ws <- create_inst_data("English (American)", "WS")
eng_wg_summary <- collapse_inst_data(eng_wg)
eng_ws_summary <- collapse_inst_data(eng_ws)
eng_comb_summary <- combine_form_data(list(eng_wg_summary, eng_ws_summary))
```


# Load predictors

Merge in the by-concept predictors (babiness, concreteness, etc) to the unilemmas and the by word predictors (phonemes) to the words/definitions.

```{r merge_unilemmas}
uni_lemmas <- get_uni_lemmas(wb_data)
uni_lemma_map <- build_uni_lemma_map(uni_lemmas)
```

```{r load_predictors}

babiness_map <- c(word = "word", babiness = "babyAVG")
babiness <- uni_lemmas |> map_predictor("babiness", babiness_map)

valence_map <- c(word = "Word", valence = "V.Mean.Sum", arousal = "A.Mean.Sum")
valence <- uni_lemmas |> map_predictor("valence", valence_map)

concreteness_map <- c(word = "Word", concreteness = "Conc.M")
concreteness <- uni_lemmas |> map_predictor("concreteness", concreteness_map)

# TODO: PHONOLOGY requires espeak
# http://espeak.sourceforge.net
#phonemes <- uni_lemmas |> map_phonemes()
# left_join(phonemes, by = c("language", "uni_lemma")) |>
```
#Load CHILDES
Loading cached CHILDES data for English:
```{r load_childes_eng}
eng_childes <- readRDS("data/childes/uni_metrics_english_(american).rds")
eng_childes
```

Loading cached CHILDES data for multiple languages:
```{r load_childes_xling}

childes_metrics <- map_df(target_langs, function(lang) {
  message(glue("Loading CHILDES data for {lang}..."))
  norm_lang <- normalize_language(lang)
  readRDS(glue("data/childes/uni_metrics_{norm_lang}.rds"))
})

```

Creating saved CHILDES data for English, potentially changing which metrics are computed and/or arguments that are passed to `childesr`:
```{r specify_childes, eval=FALSE}
metric_funs <- list(compute_count, compute_mlu, compute_positions,
                    compute_length_char, compute_length_phon)
corpus_args <- list(corpus = NULL, role = NULL, role_exclude = "Target_Child",
                    age = NULL, sex = NULL, part_of_speech = NULL, token = "*")

get_childes_metrics("English (American)", metric_funs, corpus_args)
get_uni_lemma_metrics("English (American)", uni_lemma_map)
```

Creating saved CHILDES data for many languages:
```{r create_childes_xling, eval=FALSE}
walk(target_langs, get_childes_metrics, metric_funs, corpus_args)
walk(target_langs, get_uni_lemma_metrics, uni_lemma_map)
```

The output has: 
1. raw counts of uni_lemmas (count, count_first, count_last, count_solo)
2. sum count of whole CHILDES corpus (sumcount, sumcount_first, sumcount_last, sumcount_solo)
3. freq_raw is the raw frequency (dividing count / sumcount)

# Prepare and impute
Prepare frequency
Order: Frequency, weighted, log transformed and Laplace smoothed, residualized
```{r prepare_frequency}

#Normalize frequency: log transform and smoothing (+1)
#Normalized smoothed frequencies
#the output has: 
#1. raw counts of uni_lemmas (count, count_first, count_last, count_solo)
#2. sum count of whole CHILDES corpus (sumcount, sumcount_first, sumcount_last, sumcount_solo)
#3. freq_raw is the raw frequency (dividing count / sumcount)

#Residualize frequency out of final and solo frequencies
childes_metrics<-map_df(target_langs, prepare_frequency, childes_metrics, uni_lemmas)
childes_metrics
```

Combine mapped predictors and CHILDES predictors:
```{r merge_all}
uni_joined <- uni_lemmas |>
  left_join(babiness, by = c("language", "uni_lemma")) |>
  left_join(valence, by = c("language", "uni_lemma")) |>
  left_join(concreteness, by = c("language", "uni_lemma")) |>
  left_join(childes_metrics, by = c("language", "uni_lemma"))
```

```{r impute_data}
prepped_data <- uni_joined |>
  # select out just the by lexical item data
  unnest(cols = "items") |>
  # select(-c(age, num_true, total, form, item_id)) |>
  distinct() |>
  # pull out categories from classes
  mutate(lexical_category = if_else(str_detect(lexical_class, ","), "other",
                                    lexical_class),
         # collapse v, adj, adv into one category
         lexical_category = lexical_category |> as_factor() |>
           suppressWarnings(
             fct_collapse("predicates" = c("verbs", "adjectives", "adverbs"))
             )) |>
  dplyr::select(-lexical_class)

pred_sources <- list(
  c("frequency","final_frequency", "first_frequency", "solo_frequency"),
  c("concreteness", "valence", "babiness"), 
  c("mlu"),
  c("length_char"),
  c("n_tokens"),
  c("length_char"), 
  c("n_tokens"))

imputed_data <- prepped_data |> do_full_imputation(pred_sources, 20)
imputed_data
```


# Model fitting
Aoa lm model
```{r aoa-lm}

wb_data <- wb_data |>
  mutate(num_false = total - num_true,
         prop = num_true / total) |>
  dplyr::select(language, measure, uni_lemma, prop, num_true,age, num_false, total, items) %>%
         unique()

aoas <- wb_data |>
  group_by(language, measure) |>
  nest() |>
  mutate(aoa = map(data, get_aoas, max_steps = 400)) |>
  dplyr::select(-data) |>
  unnest(cols = c(aoa))

word_values <- aoas |>
  left_join(imputed_data |>
              dplyr::select(-data) |>
              unnest(cols = c(imputed)), 
            by = c("language", "uni_lemma")) 


joined_data <- wb_data |>
  left_join(word_values, by = c("language", "measure", "uni_lemma"))

preds=list(c("frequency","mlu","final_frequency","valence", "concreteness","babiness", "first_frequency", "solo_frequency", "length_char", "n_tokens"))

#################? How to pass contrasts to lm? TODO

fitted_aoa_models <- map_df(preds, fit_models, joined_data)
fitted_aoa_models


```


age glmer model:
```{r age-glmer}
## TODO: fix fit_models; currently failing in Julia
#fitted_age_models <- fit_models(joined_data, predictors, full = TRUE)
```

# Cross-validation
```{r cross_validate}

# for simple cv result extraction
loo_df <- word_values |>
  group_nest() |>
  mutate(loo_data = map(data, crossv_loo),
         loo_models = map(data, fit_cv_models, list(make_effs_formula(predictors, FALSE, TRUE))),
         loo_preds = map2(loo_models, data, get_cv_preds),
         cv_results = map(loo_preds, get_cv_results))
loo_df

cv_results <- loo_df |>
  dplyr::select(c(language, measure, cv_results)) |>
  unnest(cols = c(cv_results))

############## plot by lex_category /abstract category and prediction error 
cv_results_pos <- loo_df |>
  dplyr::select(c(language, measure, loo_preds)) |>
  unnest(cols = c(loo_preds)) |> 
  group_by(language, lexical_category) |>
  summarise(mean_abs_dev=mean(abs_dev), mean_se=mean(se))

cv_results_cat <- loo_df |>
  dplyr::select(c(language, measure, loo_preds, data)) |>
  unnest(cols = c(loo_preds, data), names_repair = "unique") |>
  group_by(language, category) |>
  summarise(mean_abs_dev=mean(abs_dev), mean_se=mean(se))

cv_results_lex <- loo_df |>
  dplyr::select(c(language, measure, loo_preds)) |>
  unnest(cols = c(loo_preds))

eng_across_lang_lex_desc <- head(arrange(cv_results_lex %>% filter(language=="English (American)", measure=="produces"), desc(abs_dev)), 50) 
eng_across_lang_lex_desc 


```

Evaluate collinearity between predictors using variance inflation factor (VIF) of a set of predictors (pred). For a single language:
```{r vif}
eng_joined_data <- word_values |> filter(language == "English (American)")
preds <- c("frequency", "concreteness", "mlu")
vif_scores <- get_vif_bylang_bymeasure(eng_joined_data, preds)
```

Evaluate collinearity between predictors using variance inflation factor (VIF) of a set of predictors (pred). For a set of languages:
```{r vif x-ling}
preds <- c("frequency", "concreteness", "mlu")
vif_scores <- get_vif_bylang_bymeasure(word_values, preds)
```
# Plots
```{r plots1}

#####plots
lang_coefs <- fitted_aoa_models %>%
  unnest(coefficients) %>%
  mutate(signif=ifelse(p.value<0.05, TRUE, FALSE)) %>%
  filter(term %in% predictors) 
 
lang_coefs$term = factor(lang_coefs$term, levels = c("frequency", "solo_frequency", "first_frequency", "final_frequency", "mlu", "length_char", "n_tokens",
                            "babiness", "concreteness", "valence"))

lang_coefs$language = factor(lang_coefs$language, levels=c("English (American)","English (British)", "French (Quebecois)", "Spanish (Mexican)","Swedish",  "Italian", "Croatian", "Danish",  "Norwegian",  "Turkish","Russian")) #"English (Australian)",   "German", "French (French)",



#pdf(file = "data/rus_coefs.pdf",  width = 6,  height = 4) 
coefs_by_lang(lang_coefs %>% filter(language =="Russian", measure =="produces"))
#dev.off()

#pdf(file = "data/eng_coefs.pdf",   width = 5,  height = 3) 
coefs_by_lang(lang_coefs %>% filter(language=="English (American)"))
#dev.off()

#pdf(file = "data/lang_coefs.pdf",    width = 20, height = 5) 
coefs_by_lang(lang_coefs %>% filter(!language =="Russian"))
#dev.off()

```

```{r plots_langcoeff_all}

all_coefs <- fitted_aoa_models %>%
  unnest(coefficients) %>%
  mutate(signif=ifelse(p.value<0.05, TRUE, FALSE))  

all_coefs <- all_coefs %>%
  mutate(interact_lexcat=ifelse(grepl("adverbs",term),'adverbs',term))%>%
  mutate(interact_lexcat=ifelse(grepl("verbs",term),'verbs',interact_lexcat))%>%
  mutate(interact_lexcat=ifelse(grepl("other",term),'other',interact_lexcat))%>%
  mutate(interact_lexcat=ifelse(grepl("adject",term),'adjectives',interact_lexcat))%>%
  mutate(interact_lexcat=ifelse(grepl("function",term),'function_words',interact_lexcat))%>%
  mutate(interact_lexcat=ifelse(grepl("^valence|^solo_frequency|^frequency|^concreteness|^length_char|^babiness|^n_tokens|^final_frequency|^first_frequency|^mlu|Intercept",term),'single',interact_lexcat))

coefs_by_pred_all(all_coefs %>% filter(language !="Russian")) 


```


```{r plots_crossval}
#pdf(file = "data/cv_lang.pdf",    width = 8,  height = 4) 
cv_dev_lang(cv_results %>% filter(!language=="English (British)", !language=="Russian"))
#dev.off()

#pdf(file = "data/dev_words_eng_compre.pdf", width = 7, height = 5) 
dev_words(eng_across_lang_lex_desc)
#dev.off()

#pdf(file = "data/aoa_mad_lex_eng_understands.pdf", width = 7, height = 5) 
u<-aoa_mad_lex_cat(eng_across_lang_lex_desc, "English (American)", "understands", wb_data, preds)  
p<-aoa_mad_lex_cat(eng_across_lang_lex_desc, "English (American)", "produces", wb_data, preds)
plot_grid(u, p)
#dev.off()

cv_results_pos$mean_abs_dev = as.numeric(cv_results_pos$mean_abs_dev) 
ggplot(aes(x = mean_abs_dev, y =language), data = cv_results_pos %>% filter(!language=="Russian")) +
       facet_wrap(~lexical_category, nrow=5) +
       geom_point(aes(colour = factor(lexical_category)), size = 4)+
  geom_errorbar(aes(xmin=mean_abs_dev-mean_se, xmax=mean_abs_dev+mean_se))+
       geom_smooth(method = "loess") +
       scale_color_brewer(palette = "Set1") +
       theme_bw(base_size = 14) +
       theme(panel.grid = element_blank())

cv_results_cat$mean_abs_dev = as.numeric(cv_results_cat$mean_abs_dev) 
ggplot(aes(x = mean_abs_dev, y =language), data = cv_results_cat %>% filter(!language=="Russian")) +
       facet_wrap(~category) +
       geom_point(aes(colour = factor(category)), size = 4)+
  geom_errorbar(aes(xmin=mean_abs_dev-mean_se, xmax=mean_abs_dev+mean_se))+
       geom_smooth(method = "loess") +
       theme_bw(base_size = 14) +
       theme(panel.grid = element_blank())
```
