---
title: "AoA Pipeline Template---Cleaned"
format: pdf
---

# Setup
```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(dplyr.summarise.inform = FALSE)

# load libraries
## general
library(tidyverse)
library(glue)
library(here)
## data retrieval and preprocessing
library(redivis)
library(wordbankr)
library(childesr)
library(quanteda)
library(tmcn)
## modelling
library(modelr)
library(broom.mixed)
library(tidybayes)
library(bayestestR)
library(xgboost)
library(shapviz)
## visualisation
library(ggrepel)

# load functions
walk(list.files("scripts", pattern = "*.R$", full.names = TRUE), source)
set.seed(42)
theme_set(theme_mikabr(base_size = 16))
```

This template provides the structure for how to fit age of acquisition (AoA) prediction models, using data and scripts in this repository.

The general steps are:
- loading CDI data (step 1) 
- loading predictor data (step 2)
- adding your predictor(s) to the provided predictor data (step 3)
- preparing the data for modeling (step 4)
- fitting models and extract information from them (step 5)

# 1. Loading CDI data

Loading CDI data from wordbank uses the `load_wb_data()` function; this function searches for a cached version of the data, and otherwise calls `create_wb_data()` to fetch the data from Wordbank.
AoAs can be calculated from these data using `fit_aoas()`, fit using `arm::bayesglm()`.

Loading cached Wordbank data for English:
```{r load_wordbank_eng, eval=F}
eng_wb_data <- load_wb_data("English (American)")
eng_wb_data
```

Defining languages:
```{r define_langs}
target_langs <- c("Dutch",
                  "English (American)", "English (Australian)", 
                  "English (British)", 
                  "German (German)",
                  "Danish", "Norwegian", "Swedish", 
                  "French (French)", "French (Quebecois)", 
                  "Italian",
                  "Spanish (Mexican)", "Spanish (European)",
                  "Spanish (Argentinian)",
                  "Catalan",
                  "Portuguese (European)",  
                  "Croatian", "Czech", "Polish", "Russian",
                  "Turkish", 
                  "Hungarian", "Estonian", "Finnish", 
                  "Mandarin (Taiwanese)", "Mandarin (Beijing)",
                  "Cantonese",
                  "Hebrew", # "Arabic (Saudi)",
                  "Korean",
                  "Japanese")
```

Loading Wordbank data for multiple languages (cached or not):
```{r load_wordbank_xling}
wb_data <- load_wb_data(target_langs)
aoas <- fit_aoas(wb_data)
```

Creating saved Wordbank data for a language, for example:
```{r create_wordbank_eng, eval=F}
eng_wb_data <- create_wb_data("English (American)")
```

Creating saved Wordbank data one step at a time (potentially making changes between steps), for example:
```{r create_wordbank_eng_steps, eval=F}
eng_wg <- create_inst_data("English (American)", "WG")
eng_ws <- create_inst_data("English (American)", "WS")
eng_wg_summary <- collapse_inst_data(eng_wg)
eng_ws_summary <- collapse_inst_data(eng_ws)
eng_comb_summary <- combine_form_data(list(eng_wg_summary, eng_ws_summary))
```

Cache lemmas
```{r cache_lemmas, eval=F}
wb_data |> 
  select(language, uni_lemma, items) |> 
  unnest(items) |>
  distinct() |> 
  nest_by(language) |> 
  ungroup() |> 
  mutate(data = map2(data, language, 
                     \(d, l) d |> 
                       mutate(lemma = lemmatize(item_definition, l)))) |> 
  unnest(data) |> 
  write_csv(here("resources", "lemmas.csv"))
```

Example AoA plot
```{r}
df_ex <- wb_data |> 
  filter(language == "English (American)",
         measure == "produces", 
         uni_lemma %in% c("dog", "jump", "tomorrow")) |> 
  mutate(num_false = total - num_true,
         prop = num_true / total,
         prop_dist = abs(prop - 0.5))

mod_bglm <- function(df) {
  arm::bayesglm(cbind(num_true, num_false) ~ age,
                family = "binomial",
                prior.mean = .3,
                prior.scale = c(.01),
                prior.mean.for.intercept = 0,
                prior.scale.for.intercept = 2.5,
                prior.df = 1,
                data = df,
                maxit = 200)
}

mod_ex <- tibble(uni_lemma = c("dog", "jump", "tomorrow")) |> 
  mutate(mod = map(uni_lemma, \(ul) {mod_bglm(df_ex |> filter(uni_lemma == ul))}),
         preds = map(mod, \(m) {
           tibble(age = seq(8, 36, by = .2)) |> 
             mutate(prop = predict(m, newdata = tibble(age = seq(8, 36, by = .2)),
                                   type = "response"))
         })) |> 
  select(-mod) |> 
  unnest(preds)

df_ex |> 
  ggplot(aes(x = age, y = prop, col = uni_lemma)) +
  geom_hline(yintercept = .5, lty = "dashed") +
  geom_segment(aes(x = aoa, xend = aoa, yend = yend),
               data = aoas |> 
                 filter(language == "English (American)",
                        measure == "produces",
                        uni_lemma %in% c("dog", "jump", "tomorrow")) |> 
                 mutate(prop = -0.1, yend = .5),
               lty = "dashed") +
  geom_point(alpha = .6) +
  annotate("label",
           x = 17, y = 0.75, label = "dog", col = "#f8776d") +
  annotate("label",
           x = 22, y = 0.63, label = "jump", col = "#00ba38") +
  annotate("label",
           x = 33, y = 0.3, label = "tomorrow", col = "#619cff") +
  annotate("text",
           x = 8, y = 0.95, label = "English (American)", 
           hjust = 0, fontface = "italic") +
  geom_line(data = mod_ex, linewidth = 1.5) +
  coord_cartesian(ylim = c(0, 1), xlim = c(8, 36)) +
  labs(x = "Age (months)", y = "Prop. of children producing word") +
  theme(legend.position = "none")
```

```{r}
aoas |> 
  filter(measure == "produces") |> 
  group_by(uni_lemma) |> 
  summarise(n = n(),
            aoa_mean = mean(aoa),
            aoa_sd = sd(aoa)) |> 
  ggplot(aes(x = aoa_mean, y = aoa_sd)) +
  geom_point(alpha = .1)
```



# 2/3. Loading predictors and calculating metrics

Predictors can come from three main sources:
- Collected psycholinguistics norms (e.g., babiness, concreteness);
- Metrics calculated over CDI items (e.g., phonemes); or
- Metrics calculated over CHILDES, possibly with additional processing using external resources such as parsing or morphological analysis (e.g., frequency, form entropy).

## External norms

Pull out all unilemmas:
```{r merge_unilemmas}
uni_lemmas <- map_df(target_langs, extract_uni_lemmas, wb_data)
```

Emotionality is separately constructed using the `affectr` package (note that these data are already cached):
```{r emotionality_construct, eval=F}
# devtools::install_github("markallenthornton/affectr")
library(affectr)

emotionality_replace <- read_csv(here("data", "predictors", "emotionality_replace.csv"))
emotionality <- uni_lemmas |> 
  select(uni_lemma) |> 
  distinct() |> 
  filter(!uni_lemma |> str_starts("[123]")) |> 
  bind_rows(data.frame(uni_lemma = emotionality_replace$replacement)) |> 
  mutate(uni_lemma = uni_lemma |> str_replace("\\s*\\([^\\)]+\\)", ""),
         emotionality = affect3d(uni_lemma),
         rationality = emotionality[, "rationality"],
         social_impact = emotionality[, "social impact"],
         valence = emotionality[, "valence"],
         emotionality = abs(valence)) |> 
  write_csv(here("data", "predictors", "emotionality.csv"))
```

Merging in all by-concept predictors:
```{r load_predictors}
babiness_map <- c(word = "word", babiness = "babyAVG")
babiness <- uni_lemmas |> map_predictor("babiness", babiness_map)
valence_map <- c(word = "Word", valence = "V.Mean.Sum", arousal = "A.Mean.Sum")
valence <- uni_lemmas |> map_predictor("valence", valence_map)
concreteness_map <- c(word = "Word", concreteness = "Conc.M")
concreteness <- uni_lemmas |> map_predictor("concreteness", concreteness_map)
sensorimotor_map <- c(word = "Word", sensorimotor = "Minkowski3.sensorimotor")
sensorimotor <- uni_lemmas |> map_predictor("sensorimotor", sensorimotor_map)
emotionality_map <- c(word = "uni_lemma", emotionality = "emotionality")
emotionality <- uni_lemmas |> map_predictor("emotionality", emotionality_map)
# socialness_map <- c(word = "Word", socialness = "Mean")
# socialness <- uni_lemmas |> map_predictor("socialness", socialness_map)
```

## CHILDES-based metrics

### Fetching CHILDES data and parsed/morph-tagged derivatives
Get CHILDES data for many languages:
```{r get_childes, eval=F}
corpus_args <- list(corpus = NULL, role = NULL, role_exclude = "Target_Child",
                    age = NULL, sex = NULL, part_of_speech = NULL, token = "*")
```

Loading saved morphology metrics for many languages (needed for morphology and form information):
```{r create_morphs_xling, eval=F}
walk(target_langs, load_morph_data, corpus_args)
```

Loading saved parsed data for many languages (needed for subcategorisation information):
```{r parse_data, eval=F}
walk(target_langs, load_parsed_data, corpus_args = corpus_args)
```

Loading cached CHILDES metrics for English:
```{r load_childes_eng, eval=F}
eng_metrics <- load_childes_metrics("English (American)", uni_lemmas)
```

### Calculating CHILDES metrics
CHILDES metrics are calculated using functions that operate over dataframes containing CHILDES by-token/utterance information. 
Note that functions could take in just the actual CHILDES data (`base`), data that have been parsed using `udpipe` which contains lemmas, parts of speech, and Universal Dependencies tagging (`parsed`), or data with merged morphological information from UniMorph (`morph`).
We first calculate these metrics at the by-token level, then match CDI unilemmas with their possible token realisations.

Specifying which metrics will be calculated:
```{r specify_childes}
metric_funs <- list(base = list(compute_count, compute_transcript_diversity,
                                compute_mlu, compute_positions,
                                compute_length_char, compute_length_phon,
                                compute_burstiness),
                    parsed = list(compute_form_entropy, compute_subcat_entropy,
                                  compute_mdd, compute_n_features, 
                                  compute_contextual_diversity),
                    morph = list(compute_n_morphemes))
```

Creating saved CHILDES data for English:
```{r create_childes_english, eval=F}
eng_childes <- get_token_metrics("English (American)", metric_funs, corpus_args)
eng_unilemmas <- get_uni_lemma_metrics("English (American)", build_uni_lemma_map(uni_lemmas))
childes_metrics = eng_unilemmas
```

Creating saved CHILDES data for many languages:
```{r create_childes_xling, eval=F}
walk(target_langs, get_token_metrics, metric_funs, corpus_args)
```

Creating saved UNILEMMA data for many languages:
```{r create_unilemma_xling, eval=F}
walk(target_langs, get_uni_lemma_metrics, build_uni_lemma_map(uni_lemmas))
```

Loading cached CHILDES data for multiple languages:
```{r load_unilemma_xling, eval=T}
childes_metrics <- load_childes_metrics(target_langs, uni_lemmas) |> 
  filter(!is.na(uni_lemma), uni_lemma != "NA")
```

## Phonological metrics
Get phonology via eSpeak for tokens that didn't get it from CHILDES:
```{r phonology}
phon_data <- uni_lemmas |> filter(uni_lemma != "NA") |> map_phonemes()
phon_metrics <- phon_data |> compute_phon_metrics()
childes_metrics <- childes_metrics |>
  left_join(phon_metrics, by = c("language", "uni_lemma")) |>
  mutate(length_char = coalesce(length_char, num_chars),
         length_phon = coalesce(length_phon, num_phons)) |>
  select(-c(num_chars, num_phons))
```


# 4. Preparing data for modelling

## Transformations and residualisation

By default, `transform_counts()` transforms any column that starts with "count" by smoothing (add 1), normalising, and log transforming, then renaming every column "count_x" to "freq_x". 
`residualise_freqs()` residualises all columns that starts with "freq_" from the column "freq".
```{r prepare_frequency}
childes_metrics <- childes_metrics |> 
  nest(data = -language) |> 
  mutate(data = map(data, transform_counts),
         data = map(data, residualise_freqs)) |> 
  unnest()
```

We also optionally residualise predictors within category; this step was conducted in earlier versions of the pipeline, although later we opted not to residualise our predictors due to possible difficulties with downstream inference.
```{r residualise, eval=F}
semantic_preds <- c("concreteness", "babiness", "emotionality", "sensorimotor")
distrib_preds <- c("freq", "context_diversity", "burstiness")
phon_preds <- c("length_phon", "phon_neighbors")
morph_preds <- c("form_entropy", "n_features", "n_morphemes")
syntax_preds <- c("mlu", "subcat_entropy", "mdd")

childes_metrics <- childes_metrics |> 
  nest(data = -language)

for (preds in list(distrib_preds, phon_preds, morph_preds, syntax_preds)) {
  childes_metrics <- childes_metrics |> 
    mutate(data = map(data, \(d) {
      d |> mutate(across(all_of(preds[-1]), 
                         partial(residualise_col, 
                                 residualising_column = d |> pull(preds[1]))))}))
}

childes_metrics <- childes_metrics |> unnest(data)
```

## Merging and imputation

Combine mapped predictors and CHILDES predictors:
```{r merge_all}
predictor_data_list <- list(babiness, valence, concreteness, sensorimotor, 
                            emotionality, childes_metrics)
predictor_data <- predictor_data_list |>
  reduce(partial(full_join, by = c("language", "uni_lemma"))) 
```

Fixing and standardising lexical category coding:
```{r prep_data}
ref_cat = "nouns"
predictor_data_lexcat <- prep_lexcat(predictor_data, uni_lemmas, ref_cat) |>
  distinct()
```

Setting groups of predictors that come from the same information source for imputation:
```{r set_predictors}
predictor_sources <- list(
  c("freq", "burstiness", "context_diversity"),
  c("concreteness", "babiness", "emotionality", "sensorimotor"),
  c("length_phon", "phon_neighbors"),
  c("n_features", "form_entropy", "subcat_entropy", "mdd"), 
  c("n_morphemes"),
  c("mlu"))
predictors <- unlist(predictor_sources)
```

Calculating missingness rates:
```{r missingness}
missingness <- predictor_data_lexcat |> 
  group_by(language) |> 
  summarise(across(all_of(predictors), \(x) sum(is.na(x)) / n())) |> 
  pivot_longer(-c(language), names_to = "predictor", values_to = "prop_missing")
ggplot(missingness, aes(y = predictor, x = prop_missing)) +
  geom_point(aes(col = language)) +
  labs(y = "Predictor", x = "Proportion missing") +
  theme(legend.position = "bottom",
        legend.spacing.y = unit(0.1, "cm"))
```

Imputing missing data
```{r imputation}
max_steps = 20
predictor_data_imputed_scaled <- do_full_imputation(predictor_data_lexcat, 
                                                    predictor_sources, max_steps)
```

Merging predictor data with AoAs
```{r merge_aoa}
aoa_predictor_data <- predictor_data_imputed_scaled |> 
  left_join(aoas, 
            by = join_by(language, uni_lemma), 
            relationship = "many-to-many") |>
  filter(aoa <= 36, 
         lexical_category != "NA",
         lexical_category != "unknown") |> 
  rename(lexical_class = lexical_category) |> 
  mutate(lexical_category = case_when(
    category == "action_words" ~ "verbs",
    category == "descriptive_words" ~ "adjectives",
    .default = lexical_class
  ) |> 
    fct_drop() |> 
    fct_relevel(ref_cat, after = Inf) |> 
    `contrasts<-`(value = "contr.sum"))
```

Getting descriptive summaries
```{r descriptives}
n_by_lexcat <- aoa_predictor_data |> 
  group_by(language, lexical_category) |> 
  summarise(n = n())

n_by_lang <- n_by_lexcat |> 
  group_by(language) |> 
  summarise(n = sum(n))
```

# 5. Modelling

There are a range of different possible modelling approaches for AoA prediction; here we present three approaches that we have used:

i. Separate models for each language;
ii. One all-language model with random intercepts for language;
iii. A more complex XGBoost model.

## Separate language models

We fit each language separately using a `brms::brm()` model, comparing the fitted predictors.
We used this approach in several previous publications (Braginsky et al., 2019; Frank et al., 2021; Tan, Loukatou et al., 2023).
This method is intuitive and interpretable, but suffers from the problem that different predictors may have differing variance and reliabilities across languages, leading to possible non-comparability of the resultant predictors.
Nonetheless, we present it here for completeness, and because it may be useful for conducting AoA prediction for single languages.

Run models (without and with lexical category as a predictor):
```{r run_bylang_models, eval=F}
aoa_models <- fit_models(predictors, aoa_predictor_data,
                         lexcat_interactions = FALSE)
saveRDS(aoa_models, "outputs/aoa_models.rds")
saveRDS(aoa_models |> select(-model), "outputs/aoa_models_output.rds")

aoa_models_lexcat <- fit_models(predictors, aoa_predictor_data,
                                lexcat_interactions = TRUE)
saveRDS(aoa_models_lexcat, "outputs/aoa_models_lexcat.rds")
saveRDS(aoa_models_lexcat |> select(-model), "outputs/aoa_models_lexcat_output.rds")
```

```{r load_bylang_models}
aoa_models <- readRDS("outputs/aoa_models.rds")
aoa_models_lexcat <- readRDS("outputs/aoa_models_lexcat.rds")
```

Extract and tidy coefficients:
```{r bylang_coefs}
aoa_coefs <- aoa_models_lexcat |>
  select(language, measure, coefs) |>
  unnest(coefs) |>
  filter(Parameter != "b_Intercept") |>
  mutate(
    effect = if_else(str_detect(Parameter, ":"), "interaction", "main"),
    lexical_category = str_extract(Parameter, "lexical_category[0-9]"),
    term = if_else(effect == "interaction",
                   str_remove(Parameter, ":?lexical_category[0-9]:?"),
                   Parameter),
    language = factor(language, levels = target_langs)) |>
  standardise_terms() |> 
  rename(estimate = MAP,
         conf.low = CI_low,
         conf.high = CI_high)
```

```{r bylang_plot_coefs}
plot_coefs <- aoa_coefs |>
  filter(is.na(lexical_category),
         !is.na(term)) |>
  left_join(n_by_lang, by = "language") |>
  mutate(signif = ifelse(conf.low < 0 & conf.high > 0,
                         "Not significant", "Significant"))

lc_plot <- aoa_coefs |>
  mutate(lexical_category = lexical_category |> 
           replace_na("main")) |>
  select(language, measure, term, estimate, lexical_category, term_cat) |>
  pivot_wider(names_from = lexical_category, values_from = estimate) |>
  mutate(nouns = main - lexical_category1 - lexical_category2 - lexical_category3,
         adjectives = main + lexical_category1,
         function_words = main + lexical_category2,
         verbs = main + lexical_category3) |> 
  select(-c(main, lexical_category1, lexical_category2, lexical_category3)) |>
  pivot_longer(cols = c(adjectives, function_words, nouns, verbs),
               names_to = "lexical_category",
               values_to = "estimate") |>
  filter(!is.na(estimate),
         !is.na(term)) |>
  left_join(n_by_lexcat, by = c("language", "lexical_category")) |>
  mutate(lexical_category = lexical_category |> 
           factor(levels = c("nouns", "verbs", "adjectives", "function_words")) |>
           fct_relabel(label_caps))
```

Plots:
```{r bylang_main_plot}
p_bylang <- plot_coefs |> 
  filter(measure == "produces") |> 
  ggplot(aes(x = estimate, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  geom_point(aes(shape = signif, color = language),  alpha = 0.7) +
  scale_shape_manual(values = c(21, 16),
                     labels = c("Not reliable", "Reliable")) +
  stat_summary(geom = "crossbar", fun = median, fun.min = median,
               fun.max = median, fatten = 2, width = 0.5) +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", color = "Language") +
  coord_cartesian(xlim = c(-2.5, 2.5)) #+
  # theme(text = element_text(size = 20))
p_bylang
```

```{r bylang_lexcat_plot}
lc_plot |> 
  filter(measure == "produces") |> 
  ggplot(aes(x = estimate, y = term)) +
  facet_grid(term_cat ~ lexical_category, 
             scales = "free", space = "free",
             labeller = as_labeller(label_caps)) +
  geom_point(aes(color = language), alpha = 0.7) +
  scale_shape_manual(values = c(16, 21)) +
  stat_summary(geom = "crossbar", fun = mean, fun.min = mean,
               fun.max = mean, fatten = 2, width = 0.5) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", col = "Language") +
  coord_cartesian(xlim = c(-2.5, 2.5))
```

```{r}
lc_summary <- lc_plot |> 
  nest(data = c(language, estimate, n)) |> 
  mutate(est = map(data, \(d) {
    d$estimate |> mean_cl_boot()
  })) |> 
  select(-data) |> 
  unnest(est) |> 
  rename(estimate = y,
         ci.lb = ymin,
         ci.ub = ymax) |> 
  mutate(reliability = ifelse(ci.lb < 0 & ci.ub > 0,
                              "Not reliable", "Reliable"))
```


```{r}
p_bylang_lc <- lc_summary |> 
  filter(measure == "produces") |>
  mutate(lexical_category = fct_rev(lexical_category)) |> 
  ggplot(aes(x = estimate, y = term)) +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub, col = lexical_category),
                 height = 0, position = position_dodge(width = .6)) +
  geom_point(aes(col = lexical_category, shape = reliability), 
             position = position_dodge(width = .6),
             size = 2) +
  labs(x = "Coefficient estimate", y = "", 
       col = "Lexical category", shape = "Reliability") +
  coord_cartesian(xlim = c(-2.2, 2.2)) +
  scale_shape_manual(values = c(21, 16)) +
  scale_colour_discrete(breaks = c("Nouns", "Verbs", "Adjectives", "Function words")) +
  facet_grid(term_cat ~ ., 
             scales = "free", space = "free",
             labeller = as_labeller(label_caps)) #+
  #theme(text = element_text(size = 20))

p_bylang_lc
```


## All-language model

We fit one large `brms::brm()` model, partially pooling data from all languages, with random slopes for all predictors by language.
This approach allows for more reasonable estimations, with a soft regularisation for languages to have similar coefficients to each other; in practice the results are also more sensible and robust.
It is important to note the assumption that random slopes are approximately normally distributed; although this assumption is likely false since the languages in our data are not randomly sampled, in practice there is enough flexibility in the fitting process to have adequate fit for all languages.

Run model:
```{r run_alllang_model, eval=F}
aoa_predictor_alllang <- aoa_predictor_data |> 
  mutate(n_morphemes = replace_na(n_morphemes, 0))

aoa_model_alllang <- fit_all_lang_model(predictors, aoa_predictor_alllang,
                                        lexcat_interactions = TRUE)
saveRDS(aoa_model_alllang, "outputs/aoa_model_alllang.rds")
```

```{r load_alllang_model}
aoa_model_alllang <- readRDS("outputs/aoa_model_alllang.rds")
mod_all <- aoa_model_alllang$model[[1]]
mod_all_outputs <- tidy(mod_all)
```

Extract and tidy coefficients:
```{r alllang_coefs}
all_coefs <- mod_all_outputs |> 
  filter(term != "Intercept") |>
  mutate(
    effect = if_else(str_detect(term, ":"), "interaction", "main"),
    lexical_category = str_extract(term, "lexical_category[0-9]"),
    type = case_when(
      str_detect(term, "sd_") ~ "random",
      str_detect(term, "cor_") ~ "correlation",
      TRUE ~ "fixed"
    ),
    term = if_else(effect == "interaction",
                   str_remove(term, ":?lexical_category[0-9]:?"),
                   term) |>
      str_replace("neighbor", "neighbour") |> 
      str_remove("sd__") |> 
      str_remove("cor__")) |> 
  standardise_terms() |> 
  filter(type != "correlation")

all_draws <- gather_draws(mod_all, `b_.*`, `r_.*`, regex = TRUE) |> 
  separate_wider_delim(.variable,
                       names = c("variable", "language", "measure"),
                       delim = regex("[\\[\\],]"),
                       too_few = "align_start",
                       too_many = "drop")
all_draws_fixed <- all_draws |> 
  filter(str_starts(variable, "b_")) |> 
  mutate(variable = str_remove(variable, "b_"))
all_draws_random <- all_draws |>
  filter(str_starts(variable, "r_"))

all_draws_est <- all_draws_random |> 
  left_join(all_draws_fixed |> select(-language, -measure), 
            by = join_by(.chain, .iteration, .draw, measure == variable)) |> 
  mutate(estimate = .value.x + .value.y)

all_langs_est <- all_draws_est |> 
  group_by(language, measure) |> 
  summarise_draws()
all_fixed_est <- all_draws_fixed |> 
  group_by(variable) |> 
  rename(estimate = .value) |> 
  summarise_draws()
```

Plot:
```{r alllang_plot_coefs}
plot_all_langs <- all_langs_est |> 
  filter(!str_detect(measure, "lexical_category"),
         measure != "Intercept") |> 
  rename(term = measure) |> 
  mutate(language = str_replace_all(language, "\\.", " ") |> 
           factor(levels = target_langs),
         reliability = ifelse(reliability, "Reliable", "Not reliable")) |> 
  standardise_terms()
plot_fixed <- all_fixed_est |> 
  filter(!str_detect(variable, "lexical_category"),
         variable != "Intercept") |> 
  rename(term = variable) |> 
  standardise_terms()
```

```{r alllang_main_plot}
plot_all_langs |> 
  ggplot(aes(x = map, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_point(aes(col = language, shape = reliability), 
             alpha = .7, size = 2) +
  geom_crossbar(aes(xmin = map, xmax = map), 
                width = 0.5, fatten = 2,
                data = plot_fixed) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", color = "Language") +
  coord_cartesian(xlim = c(-2.5, 2.5)) +
  scale_shape_manual(values = c(21, 16))
```

Extract and tidy lexical category coefficients:
```{r alllang_lexcat_coefs}
all_langs_lexcat_est <- all_draws_est |> 
  mutate(lexcat = str_extract(measure, "lexical_category[0-9]") |> 
           replace_na("main"),
         measure = str_remove(measure, ":?lexical_category[0-9]:?"),
         measure = ifelse(measure == "", "Intercept", measure)) |> 
  select(-.value.x, -.value.y) |>
  pivot_wider(names_from = lexcat, values_from = estimate) |> 
  mutate(nouns = main - lexical_category1 - lexical_category2 - lexical_category3,
         adjectives = main + lexical_category1,
         function_words = main + lexical_category2,
         verbs = main + lexical_category3) |> 
  select(-main, -lexical_category1, -lexical_category2, -lexical_category3) |> 
  pivot_longer(cols = c(nouns, adjectives, verbs, function_words),
               names_to = "lexical_category",
               values_to = "estimate") |> 
  group_by(language, measure, lexical_category) |> 
  summarise_draws()

all_fixed_lexcat_est <- all_draws_fixed |> 
  mutate(measure = variable,
         lexcat = str_extract(measure, "lexical_category[0-9]") |> 
           replace_na("main"),
         measure = str_remove(measure, ":?lexical_category[0-9]:?"),
         measure = ifelse(measure == "", "Intercept", measure)) |> 
  select(-variable) |> 
  rename(estimate = .value) |>
  pivot_wider(names_from = lexcat, values_from = estimate) |> 
  mutate(nouns = main - lexical_category1 - lexical_category2 - lexical_category3,
         adjectives = main + lexical_category1,
         function_words = main + lexical_category2,
         verbs = main + lexical_category3) |> 
  select(-main, -lexical_category1, -lexical_category2, -lexical_category3) |> 
  pivot_longer(cols = c(nouns, adjectives, verbs, function_words),
               names_to = "lexical_category",
               values_to = "estimate") |> 
  group_by(measure, lexical_category) |> 
  summarise_draws()

plot_all_langs_lexcat <- all_langs_lexcat_est |> 
  filter(measure != "Intercept") |> 
  rename(term = measure) |> 
  mutate(language = str_replace_all(language, "\\.", " ") |>
           factor(levels = target_langs),
         reliability = ifelse(reliability, "Reliable", "Not reliable"),
         lexical_category = lexical_category |> 
           factor(levels = c("nouns", "verbs", "adjectives", "function_words")) |> 
           fct_relabel(label_caps)) |> 
  standardise_terms()

plot_all_fixed_lexcat <- all_fixed_lexcat_est |> 
  filter(measure != "Intercept") |> 
  rename(term = measure) |> 
  ungroup() |> 
  mutate(reliability = ifelse(reliability, "Reliable", "Not reliable"),
         lexical_category = lexical_category |> 
           factor(levels = c("nouns", "verbs", "adjectives", "function_words")) |> 
           fct_relabel(label_caps)) |> 
  standardise_terms()
```

Plot (both canonical and reduced plots):
```{r alllang_lexcat_plot}
plot_all_langs_lexcat |> 
  ggplot(aes(x = map, y = term)) +
  facet_grid(term_cat ~ lexical_category, 
             scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_point(aes(col = language, shape = reliability), alpha = .7) +
  geom_crossbar(aes(xmin = map, xmax = map), 
                width = 0.5, fatten = 2,
                data = plot_all_fixed_lexcat) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", color = "Language") +
  coord_cartesian(xlim = c(-3.5, 3.5)) +
  scale_shape_manual(values = c(21, 16)) +
  theme(legend.position = "none")
```

```{r alllang_lexcat_plot_condensed}
plot_all_fixed_lexcat |> 
  arrange(lexical_category, term_cat, term) |> 
  mutate(lexical_category = fct_rev(lexical_category)) |> 
  ggplot(aes(x = map, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_errorbarh(aes(xmin = hdi.lower, xmax = hdi.upper, 
                     col = lexical_category, 
                     group = lexical_category), height = 0.2,
                 position = position_dodge(width = .4)) +
  geom_point(aes(shape = reliability, col = lexical_category, 
                 group = lexical_category), size = 2.5,
             position = position_dodge(width = .4)) +
  # geom_path(aes(group = lexical_category, col = lexical_category), 
  #           position = position_dodge(width = .4)) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", col = "Lexical category") +
  coord_cartesian(xlim = c(-2, 2)) +
  scale_shape_manual(values = c(21, 16)) +
  scale_colour_discrete(breaks = c("Nouns", "Verbs", "Adjectives", "Function words"))
```

## XGBoost model

We fit an XGBoost model, which is more complex in that it allows for arbitrary higher-order interactions among predictors.
We shift from an estimation to a prediction approach; this move trades direct interpretability (of coefficients) for better power.
Our approach involves 5-fold cross-validation to find the best hyperparameters, followed by the refitting of a model with all the data using the best hyperparameter setting.
We interpret the resultant models using SHAP values.

Prepare data:
```{r xgboost_data_prep}
# aoa_pred_data_xgb <- aoa_predictor_data |> 
#   select(language, lexical_category, all_of(predictors)) |> 
#   mutate(across(all_of(predictors), as.numeric),
#          lexical_category = lexical_category |> factor() |> as.integer(),
#          language = language |> factor() |> as.integer()) |> 
#   as.matrix()
aoa_data_xgb <- aoa_predictor_data |> 
  nest(data = -measure) |>
  mutate(pred_data = map(data, \(d) d |> 
                       select(language, lexical_category, all_of(predictors)) |> 
                       mutate(across(all_of(predictors), as.numeric),
                              lexical_category = lexical_category |> factor() |> as.integer(),
                              language = language |> factor() |> as.integer())),
         out_data = map(data, \(d) d |> pull(aoa)),
         dmat = map2(pred_data, out_data, 
                     \(pd, od) xgb.DMatrix(data = pd, label = od)))

# aoa_pred_data_xgb_df_prod <- aoa_predictor_data |> 
#   filter(measure == "produces") |> 
#   select(language, lexical_category, all_of(predictors)) |> 
#   mutate(across(all_of(predictors), as.numeric),
#          lexical_category = lexical_category |> factor() |> as.integer(),
#          language = language |> factor() |> as.integer())
# aoa_out_data_xgb_prod <- aoa_predictor_data |> 
#   filter(measure == "produces") |> 
#   pull(aoa)
# 
# # aoa_dtrain <- xgb.DMatrix(data = aoa_pred_data_xgb, label = aoa_out_data_xgb)
# aoa_pred_dmat <- xgb.DMatrix(data = aoa_pred_data_xgb_df, label = aoa_out_data_xgb)
```

Cross-validation and hyperparameter search:
```{r xgb_cv, eval=F}
hyper_grid <- expand.grid(
  objective = "reg:squarederror",
  eval_metric = "rmse",
  learning_rate = 0.1,
  max_depth = 3:6, 
  min_child_weight = 3,
  subsample = 0.5, 
  colsample_bytree = 0.5,
  min_split_loss = c(0, 1, 10, 100, 1000),
  reg_lambda = c(0, 1e-2, 0.1, 1, 10, 100),
  reg_alpha = c(0, 1e-2, 0.1, 1, 10, 100, 1000)
) |> 
  mutate(objective = as.character(objective),
         eval_metric = as.character(eval_metric))

aoa_mod_xgb <- aoa_data_xgb |> 
  select(measure, dmat) |> 
  mutate(hyper_grid = map(dmat, \(dmat) {
    hyper_grid |> 
      mutate(rmse = map_dbl(seq_len(nrow(hyper_grid)), \(i) {
        set.seed(123)
        message("Fitting model ", i, " of ", nrow(hyper_grid))
        params <- hyper_grid[i,] |> 
          as.list()
        
        aoa_xgb_cv <- xgb.cv(params = params,
                             data = dmat, 
                             nrounds = 1000, 
                             nfold = 5,
                             verbose = FALSE,
                             early_stopping_rounds = 50)
        min(aoa_xgb_cv$evaluation_log$test_rmse_mean)
      }))
  }))

# hyper_grid$rmse <- map_dbl(seq_len(nrow(hyper_grid)), \(i) {
#   set.seed(123)
#   message("Fitting model ", i, " of ", nrow(hyper_grid))
#   params <- hyper_grid[i,] |> 
#     as.list()
#   
#   aoa_xgb_cv <- xgb.cv(params = params,
#                        data = aoa_pred_dmat, 
#                        nrounds = 1000, 
#                        nfold = 5,
#                        verbose = FALSE,
#                        early_stopping_rounds = 50)
#   min(aoa_xgb_cv$evaluation_log$test_rmse_mean)
# })

aoa_mod_xgb_outputs <- aoa_mod_xgb |> 
  select(measure, hyper_grid) |> 
  unnest(hyper_grid)

write_csv(aoa_mod_xgb_outputs, "outputs/xgb_hyperparam_grid.csv")
```

Run final model
```{r xgb_final_model}
aoa_mod_xgb_outputs <- read_csv("outputs/xgb_hyperparam_grid.csv")

best_xgb_params <- aoa_mod_xgb_outputs |>
  group_by(measure) |> 
  filter(rmse == min(rmse)) |>
  select(-rmse)

aoa_xgb_models <- aoa_data_xgb |> 
  left_join(best_xgb_params |> nest(params = -measure), by = "measure") |>
  mutate(model = map2(dmat, params,
                      \(dmat, params) {
                        xgb.train(data = dmat,
                                  nrounds = 1000,
                                  params = as.list(params))
                      }))
```

Get SHAP values
```{r xgb_shap}
aoa_shap <- aoa_xgb_models |> 
  mutate(shap = map2(model, pred_data,
                      \(model, pred_data) {
                        shapviz(model,
                                X_pred = data.matrix(pred_data),
                                interaction = TRUE)
                      }))

# shap <- shapviz(aoa_xgb_model,
#                 X_pred = data.matrix(aoa_pred_data_xgb_df),
#                 interaction = TRUE)
```

```{r xgb_shap_plot}
sv_importance(aoa_shap$shap[[1]], max_display = 20)
```

```{r xgb_shap_beeswarm}
sv_importance(aoa_shap$shap[[1]], kind = "bee", max_display = 20)
```

# 6. Further analyses
## Cross-linguistic correlations
We analysed the correlations between predictor estimates across languages. This was only possible with the separate language models (the all-language models had non-independence of estimations due to partial pooling).
```{r}
morph_complexity <- read_csv(here("data", "morph_complexity.csv"))
```

```{r correlations}
cor_coefs <- aoa_coefs |> 
  filter(is.na(lexical_category),
         !is.na(term),
         measure == "produces") |> 
  select(language, term, estimate) |> 
  mutate(language = str_replace(language, "\\.", " ") |> 
           factor(levels = target_langs)) |> 
  arrange(language)

cor_matrix <- cor_coefs |>
  pivot_wider(names_from = term, values_from = estimate) |> 
  ungroup() |> 
  select(-language) |> 
  as.matrix() |> 
  `rownames<-`(cor_coefs |> pull(language) |> unique())
```

```{r correlations_tidy}
cor_long <- cor(t(cor_matrix), use = "pairwise.complete.obs") |> 
  as_tibble(rownames = "language_1") |>
  pivot_longer(cols = -language_1, names_to = "language_2") |>
  left_join(morph_complexity |> select(language, family_1 = language_family),
            by = c("language_1" = "language")) |>
  left_join(morph_complexity |> select(language, family_2 = language_family),
            by = c("language_2" = "language"))
```

```{r correlations_summary}
cor_gen <- cor_long |>
  filter(language_1 != language_2) |>
  group_by(language_1) |>
  summarise(estimate = mean(value),
            ci.lb = mean(value) - 0.95 * sd(value) / sqrt(n()),
            ci.ub = mean(value) + 0.95 * sd(value) / sqrt(n()))

cor_fam <- cor_long |>
  filter(language_1 != language_2,
         family_1 == family_2) |>
  group_by(language_1) |>
  summarise(estimate = mean(value),
            ci.lb = mean(value) - 0.95 * sd(value) / sqrt(n()),
            ci.ub = mean(value) + 0.95 * sd(value) / sqrt(n()))

cor_rand <- lapply(seq(100), \(i) {
  apply(cor_matrix, 1, sample) |>
    cor(use = "pairwise.complete.obs") |>
    as_tibble(rownames = "language_1") |>
    pivot_longer(cols = -language_1, names_to = "language_2") |>
    filter(language_1 != language_2) |>
    mutate(sim = i)}) |>
  bind_rows() |>
  group_by(language_1) |>
  summarise(estimate = mean(value),
            ci.lb = mean(value) - 0.95 * sd(value) / sqrt(n()),
            ci.ub = mean(value) + 0.95 * sd(value) / sqrt(n()))

cor_all <- cor_gen |>
  left_join(cor_fam, by = "language_1", suffix = c("", "_fam")) |>
  left_join(cor_rand, by = "language_1", suffix = c("_gen", "_rand")) |>
  rename(language = language_1) |>
  left_join(morph_complexity |> select(language, language_family), 
            by = join_by(language)) |>
  mutate(language = factor(language, target_langs) |> fct_rev()) |>
  arrange(desc(language)) |>
  mutate(language_family = as_factor(language_family))
```

```{r correlations-plot}
GERMANIC <- "#cc0000"
ROMANCE <- "#e69138"
SLAVIC <- "#f1c232"
SINOTIBETAN <- "#8db63d"
URALIC <- "#45816e"
JAPONIC <- "#3d85c6"
KOREANIC <- "#3d50c6"
SEMITIC <- "#674ea7"
TURKIC <- "#cd3d9a"
FAM_SCALE <- c(GERMANIC, ROMANCE, SLAVIC, SINOTIBETAN,
               URALIC, JAPONIC, KOREANIC, SEMITIC, TURKIC)

cor_all_long <- cor_all |> 
  mutate(language = factor(language, levels = target_langs) |> fct_rev(),
         language_family = language_family |> fct_relevel("Germanic")) |> 
  pivot_longer(cols = -c(language, language_family),
               names_to = c("estimate", "type"),
               names_sep = "_",
               values_to = "value") |> 
  pivot_wider(names_from = estimate, values_from = value)

p_cor <- cor_all_long |> 
  filter(type != "rand") |>
  ggplot(aes(y = language, col = language_family)) +
  geom_vline(xintercept = mean(cor_all$estimate_gen),
             color = "grey", linetype = "dotted") +
  geom_pointrange(aes(x = estimate, xmin = ci.lb, xmax = ci.ub, shape = type)) +
  geom_boxplot(aes(xlower = ci.lb, xupper = ci.ub, xmiddle = estimate,
                   xmin = ci.lb, xmax = ci.ub,
                   fill = language_family),
               stat = "identity", col = "#FFFFFF00",
               data = cor_all_long |> filter(type == "rand")) +
  scale_colour_manual(values = FAM_SCALE, guide = "none") +
  scale_fill_manual(values = FAM_SCALE, guide = "none") +
  scale_shape_manual(labels = c("Correlation within family", "Correlation across all languages"), 
                     values = c(21, 16)) +
  labs(x = "Correlation",
       y = "Language",
       shape = "Correlation type") +
  theme(text = element_text(size = 20),
        legend.position = "bottom",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))
p_cor
```

```{r}
cor_all_long |> 
  select(language, type, estimate) |> 
  pivot_wider(names_from = type, values_from = estimate) |> 
  mutate(within_better = fam > gen) |> 
  count(within_better)
```


## Morphological complexity
We use the random slopes from the separate language models to examine the relationship between morphological complexity and the effect of morphosyntactic predictors on AoA.
```{r morph_complexity_bylang}
ms_terms <- c("N features", "Form entropy", "N morphemes", "MLU-w", "MDD", "Subcat entropy") 

morph_coefs <- lc_plot |> 
  filter(term %in% ms_terms) |> 
  nest(data = -language) |> 
  mutate(iso_codes = sapply(language, convert_lang_morph_complexity)) |> 
  left_join(morph_complexity) |> 
  unnest(data) |> 
  select(-iso_codes) |> 
  mutate(term = as.factor(term))

lexcats <- c("Nouns", "Verbs", "Adjectives", "Function words")

mc_mods_lc <- map(c("produces", "understands"), \(y) {
  map(ms_terms, \(x) {
    map(lexcats, \(lc) {
      arm::bayesglm(estimate ~ morph_complexity, 
       data = morph_coefs |> 
         filter(term == x, measure == y, 
                lexical_category == lc))
    })
  }) |> unlist(recursive = FALSE)
}) |> unlist(recursive = FALSE)
saveRDS(mc_mods_lc, "outputs/mc_mods_bylang.rds")

mc_vals_lc <- expand_grid(measure = c("produces", "understands"),
                       ms_term = ms_terms,
                       lexical_category = lexcats) |> 
  mutate(mc_data = map(mc_mods_lc, broom.mixed::tidy)) |> 
  unnest(mc_data) |> 
  mutate(ci.low = estimate - std.error,
         ci.high = estimate + std.error,
         signif = !(ci.low < 0 & ci.high > 0))
```

```{r}
mlu_pred <- lc_plot |>
  filter(term == "MLU-w",
         lexical_category == "Verbs",
         measure == "produces") |>
  left_join(morph_complexity |>
              select(language, iso_unique, morph_complexity)) |>
  mutate(language = factor(language, levels = target_langs))

ggplot(mlu_pred, aes(x = morph_complexity, y = estimate)) +
  geom_point(aes(col = language)) + 
  geom_smooth(method = "lm", col = "black") +
  geom_hline(yintercept = 0, color = "grey", lty = "dotted") +
  geom_label_repel(aes(label = iso_unique, col = language), size = 3.5) +
  labs(x = "Estimated morphological complexity", 
       y = "Coefficient estimate",
       col = "Language") +
  theme_mikabr() +
  theme(legend.position = "none")
```

```{r}
mc_vals_lc |> 
  filter(term == "morph_complexity",
         measure == "produces") |>
  mutate(lexical_category = factor(lexical_category, levels = lexcats) |> 
           fct_rev(),
         reliability = ifelse(signif, "Reliable", "Not reliable")) |> 
  arrange(ms_term, lexical_category) |> 
  ggplot(aes(x = estimate, y = ms_term, col = lexical_category)) +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2, col = NA) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  geom_errorbar(aes(xmin = ci.low, xmax = ci.high), 
                width = 0,
                position = position_dodge(.4)) +
  geom_point(aes(shape = reliability, group = lexical_category),
             position = position_dodge(.4)) +
  scale_shape_manual(values = c(1, 16)) +
  guides(colour = guide_legend(reverse = TRUE)) +
  labs(x = "Morphosyntactic complexity effect",
       y = "",
       col = "Lexical category",
       shape = "Reliability")
```

Overall
```{r}
morph_coefs_fixed <- plot_coefs |> 
  filter(term %in% ms_terms) |> 
  left_join(morph_complexity, by = join_by(language)) |> 
  mutate(term = as.factor(term))

mc_mods <- map(c("produces", "understands"), \(y) {
  map(ms_terms, \(x) {
    arm::bayesglm(estimate ~ morph_complexity, 
                  data = morph_coefs |> 
                    filter(term == x, measure == y))
  })
}) |> unlist(recursive = FALSE)
saveRDS(mc_mods, "outputs/mc_mods_bylang_fixed.rds")

mc_vals <- expand_grid(measure = c("produces", "understands"),
                       ms_term = ms_terms) |> 
  mutate(mc_data = map(mc_mods, broom.mixed::tidy)) |> 
  unnest(mc_data) |> 
  mutate(ci.low = estimate - std.error,
         ci.high = estimate + std.error,
         signif = !(ci.low < 0 & ci.high > 0))
```

```{r}
p_morph <- morph_coefs_fixed |> 
  filter(measure == "produces") |> 
  left_join(mc_vals |> 
              filter(term == "morph_complexity", 
                     measure == "produces") |> 
              mutate(reliability = ifelse(signif, "Reliable", "Not reliable")) |> 
              select(term = ms_term, reliability),
            by = join_by(term)) |> 
  mutate(term = factor(term, levels = ms_terms)) |> 
  ggplot(aes(x = morph_complexity, y = estimate)) +
  facet_wrap(term ~ .) +
  geom_hline(yintercept = 0, color = "grey", lty = "dotted") +
  geom_smooth(aes(lty = reliability), method = "lm", col = "#000000") +
  geom_point(aes(col = language), alpha = 0.7) +
  scale_colour_discrete(guide = "none") +
  scale_linetype_manual(values = c("dashed", "solid")) +
  labs(x = "Morphological complexity", y = "Coefficient estimate",
       lty = "Reliability") +
  theme(text = element_text(size = 20),
        legend.position = "bottom",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))
p_morph
```


