---
title: "AoA prediction template"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(dplyr.summarise.inform = FALSE)
# load libraries
library(tidyverse)
library(modelr)
library(glue)
library(wordbankr)
library(childesr)
library(here)
library(quanteda)
library(tmcn)
# load functions
walk(list.files("scripts", pattern = "*.R$", full.names = TRUE), source)
set.seed(42)
```

This template provides the structure for how to fit age of acquisition (AoA) prediction models, using data and scripts in this repository.

The general steps are:
- loading the provided CDI data and predictor data
- adding your predictor(s) to the provided predictor data
- using the functions in `scripts/prep_data.R` to prepare the data for modeling
- using the functions in `scripts/fit_models.R` to fit models and extract information from them


# Load Wordbank data

Loading cached Wordbank data for English:
```{r load_wordbank_eng, eval=FALSE}
eng_wb_data <- load_wb_data("English (American)")
eng_wb_data
```

Defining languages:
```{r define_langs}
target_langs <- c("French (French)", "French (Quebecois)", 
                  "Italian",
                  "Spanish (Mexican)", "Spanish (European)",
                  "Catalan",
                  "Portuguese (European)",  
                  "Dutch",
                  "English (American)", "English (Australian)", 
                  "English (British)", 
                  "German",
                  "Danish", "Norwegian", "Swedish", 
                  "Croatian", "Czech", "Russian",
                  "Turkish", 
                  "Hungarian", "Estonian", "Finnish", 
                  "Mandarin (Taiwanese)", "Mandarin (Beijing)",
                  "Cantonese",
                  "Hebrew", # "Arabic (Saudi)",
                  "Korean",
                  "Japanese")
```


Loading Wordbank data for multiple languages (cached or not):
```{r load_wordbank_xling}
wb_data <- load_wb_data(target_langs, db_args = db_args)
aoas <- fit_aoas(wb_data)
```

Creating saved Wordbank data for a language, for example:
```{r create_wordbank_eng, eval=FALSE}
eng_wb_data <- create_wb_data("English (American)")
```

Creating saved Wordbank data one step at a time (potentially making changes between steps), for example:
```{r create_wordbank_eng_steps, eval=FALSE}
eng_wg <- create_inst_data("English (American)", "WG")
eng_ws <- create_inst_data("English (American)", "WS")
eng_wg_summary <- collapse_inst_data(eng_wg)
eng_ws_summary <- collapse_inst_data(eng_ws)
eng_comb_summary <- combine_form_data(list(eng_wg_summary, eng_ws_summary))
```

Cache lemmas
```{r, eval=F}
wb_data |> 
  select(language, uni_lemma, items) |> 
  unnest(items) |>
  distinct() |> 
  nest_by(language) |> 
  ungroup() |> 
  mutate(data = map2(data, language, 
                     \(d, l) d |> 
                       mutate(lemma = lemmatize(item_definition, l)))) |> 
  unnest(data) |> 
  write_csv(here("resources", "lemmas.csv"))
```


# Load predictors

## Ratings and phonemes

Merge in the by-concept predictors (babiness, concreteness, etc) to the unilemmas and the by word predictors (phonemes) to the words/definitions.

```{r merge_unilemmas}
uni_lemmas <- map_df(target_langs, extract_uni_lemmas, wb_data)
```

```{r load_predictors}
babiness_map <- c(word = "word", babiness = "babyAVG")
babiness <- uni_lemmas |> map_predictor("babiness", babiness_map)
valence_map <- c(word = "Word", valence = "V.Mean.Sum", arousal = "A.Mean.Sum")
valence <- uni_lemmas |> map_predictor("valence", valence_map)
concreteness_map <- c(word = "Word", concreteness = "Conc.M")
concreteness <- uni_lemmas |> map_predictor("concreteness", concreteness_map)
sensorimotor_map <- c(word = "Word", sensorimotor = "Minkowski3.sensorimotor")
sensorimotor <- uni_lemmas |> map_predictor("sensorimotor", sensorimotor_map)
```

```{r emotionality_construct, eval=F}
emotionality_replace <- read_csv(here("data", "predictors", "emotionality_replace.csv"))
emotionality <- uni_lemmas |> 
  select(uni_lemma) |> 
  distinct() |> 
  filter(!uni_lemma |> str_starts("[123]")) |> 
  bind_rows(data.frame(uni_lemma = emotionality_replace$replacement)) |> 
  mutate(uni_lemma = uni_lemma |> str_replace("\\s*\\([^\\)]+\\)", ""),
         emotionality = affect3d(uni_lemma),
         rationality = emotionality[, "rationality"],
         social_impact = emotionality[, "social impact"],
         valence = emotionality[, "valence"],
         emotionality = abs(valence)) |> 
  write_csv(here("data", "predictors", "emotionality.csv"))
```

```{r}
emotionality_map <- c(word = "uni_lemma", emotionality = "emotionality")
emotionality <- uni_lemmas |> map_predictor("emotionality", emotionality_map)
```

## CHILDES

Get CHILDES data for many languages:
```{r get_childes, eval=FALSE}
corpus_args <- list(corpus = NULL, role = NULL, role_exclude = "Target_Child",
                    age = NULL, sex = NULL, part_of_speech = NULL, token = "*")
```


Loading saved morphology metrics for many languages:
```{r create_morphs_xling, eval=FALSE}
walk(target_langs, load_morph_data, corpus_args)
```

Loading saved parsed data for many languages:
```{r parse_data, eval=FALSE}
walk(target_langs, load_parsed_data, corpus_args = corpus_args)
```


Loading cached CHILDES metrics for English:
```{r load_childes_eng, eval=FALSE}
eng_metrics <- load_childes_metrics("English (American)", uni_lemmas)
```

Creating saved CHILDES metrics for English, potentially changing which metrics are computed and/or arguments that are passed to `childesr` functions:
```{r specify_childes}
metric_funs <- list(base = list(compute_count, compute_transcript_diversity,
                                compute_mlu, compute_positions,
                                compute_length_char, compute_length_phon,
                                compute_burstiness),
                    parsed = list(compute_form_entropy, compute_subcat_entropy,
                                  compute_n_features, compute_contextual_diversity),
                    morph = list(compute_n_morphemes))
```


Creating saved CHILDES data for English:
```{r create_childes_english, eval=FALSE}
eng_childes <- get_token_metrics("English (American)", metric_funs, corpus_args)
eng_unilemmas <- get_uni_lemma_metrics("English (American)", build_uni_lemma_map(uni_lemmas))
childes_metrics = eng_unilemmas
```


Creating saved CHILDES data for many languages:
```{r create_childes_xling, eval=FALSE}
walk(target_langs, get_token_metrics, metric_funs, corpus_args)
```

Creating saved UNILEMMA data for many languages:
```{r create_unilemma_xling, eval=FALSE}
walk(target_langs, get_uni_lemma_metrics, build_uni_lemma_map(uni_lemmas))
```

Loading cached CHILDES data for multiple languages:
```{r load_unilemma_xling, eval=TRUE}
childes_metrics <- load_childes_metrics(target_langs, uni_lemmas) |> 
  filter(!is.na(uni_lemma), uni_lemma != "NA")
```


Get phonology via eSpeak for tokens that didn't get it from CHILDES:
```{r eval=TRUE}
phon_data <- uni_lemmas |> filter(uni_lemma != "NA") |> map_phonemes()
phon_metrics <- phon_data |> compute_phon_metrics()
childes_metrics <- childes_metrics |>
  left_join(phon_metrics, by = c("language", "uni_lemma")) |>
  mutate(length_char = coalesce(length_char, num_chars),
         length_phon = coalesce(length_phon, num_phons)) |>
  select(-c(num_chars, num_phons))
```


# Prepare data for modeling

## Frequency transformations

By default, `transform_counts()` transforms any column that starts with "count" by smoothing (add 1), normalizing, and log transforming, then renaming every column "count_x" to "freq_x". `residualise_freqs()` residualises all columns that starts with "freq_" from the column "freq".

```{r prepare_frequency}
childes_metrics <- childes_metrics |> 
  nest(data = -language) |> 
  mutate(data = map(data, transform_counts),
         data = map(data, residualise_freqs))
```

```{r residualise, eval=F}
semantic_preds <- c("concreteness", "babiness", "emotionality", "sensorimotor")
distrib_preds <- c("freq", "context_diversity", "burstiness")
phon_preds <- c("length_phon", "phon_neighbors")
morph_preds <- c("form_entropy", "n_features", "n_morphemes")
syntax_preds <- c("mlu", "subcat_entropy")

for (preds in list(distrib_preds, phon_preds, morph_preds, syntax_preds)) {
  childes_metrics <- childes_metrics |> 
    mutate(data = map(data, \(d) {
      d |> mutate(across(all_of(preds[-1]), 
                         partial(residualise_col, 
                                 residualising_column = d |> pull(preds[1]))))}))
}
```

```{r}
childes_metrics <- childes_metrics |> unnest(data)
```


## Combining sources

Combine mapped predictors and CHILDES predictors:

```{r merge_all}
predictor_data_list <- list(babiness, valence, concreteness, sensorimotor, 
                            emotionality, childes_metrics)
predictor_data <- predictor_data_list |>
  reduce(partial(full_join, by = c("language", "uni_lemma"))) 
```

## Setting predictors

```{r set_predictors}
predictor_sources <- list(
  c("freq", "burstiness", "context_diversity"), # "cd"
  c("concreteness", "babiness", "emotionality", "sensorimotor"),
  c("length_phon", "phon_neighbors"),
  c("n_features", "form_entropy", "subcat_entropy"), 
  c("n_morphemes"),
  c("mlu"))# ,
  # c("semantic_diversity", "semantic_support"))
predictors <- unlist(predictor_sources)
```


## Preparing data for regression

```{r prep_data}
ref_cat = "nouns"
predictor_data_lexcat <- prep_lexcat(predictor_data, uni_lemmas, ref_cat) |>
  distinct()
```

```{r}
missingness <- predictor_data_lexcat |> 
  group_by(language) |> 
  summarise(across(all_of(predictors), \(x) sum(is.na(x)) / n())) |> 
  pivot_longer(-c(language), names_to = "predictor", values_to = "prop_missing")
ggplot(missingness, aes(y = predictor, x = prop_missing)) +
  geom_point(aes(col = language)) +
  labs(y = "Predictor", x = "Proportion missing") +
  theme(legend.position = "bottom")
```


```{r prep_data2}
max_steps = 20
predictor_data_imputed_scaled <- do_full_imputation(predictor_data_lexcat, predictor_sources, max_steps)
```

```{r}
# specific handling for subcat_entropy for non-verbs
# predictor_data_imputed_scaled <- predictor_data_imputed_scaled |> 
#   mutate(subcat_entropy = ifelse(lexical_category == "verbs", subcat_entropy, 0))
```

## Merge with AOAs

```{r merge_aoa}
aoa_predictor_data <- predictor_data_imputed_scaled |> 
  left_join(aoas, by = c("language", "uni_lemma"), relationship = "many-to-many") |>
  filter(aoa <= 36, 
         lexical_category != "NA",
         lexical_category != "unknown") |> 
  mutate(lexical_category = lexical_category |> 
           fct_drop() |> 
           fct_relevel(ref_cat, after = Inf) |> 
           `contrasts<-`(value = "contr.sum"))
```

# Modelling

## Run model 

```{r, eval=T}
aoa_models <- fit_models(predictors, aoa_predictor_data,
                         lexcat_interactions = FALSE)
saveRDS(aoa_models, "aoa_models.rds")
saveRDS(aoa_models |> select(-model), "aoa_models_output.rds")
aoa_models_lexcat <- fit_models(predictors, aoa_predictor_data,
                                lexcat_interactions = TRUE)
saveRDS(aoa_models_lexcat, "aoa_models_lexcat.rds")
saveRDS(aoa_models_lexcat |> select(-model), "aoa_models_lexcat_output.rds")
```

```{r}
aoa_models <- readRDS("aoa_models.rds")
aoa_models_lexcat <- readRDS("aoa_models_lexcat.rds")
```


## Model outputs

Coefficients:
```{r}
coefs <- aoa_models |> select(language, measure, coefs) |> unnest(coefs) 
```

```{r extract_coefs}
lexcats <- set_names(
  paste0("lexical_category", 1:2),
  rownames(contrasts(aoa_models_lexcat$group_data[[1]]$lexical_category))[1:2]
)

display_predictors <- function(predictors) {
  predictors |>
    str_replace_all("b_", "") |>
    str_replace_all("_", " ") |>
    str_to_sentence() |>
    str_replace("Mlu", "MLU-w") |>
    str_replace("Length phon", "Length in phonemes") |>
    str_replace("Freq", "Frequency") |>
    str_replace("Cd", "Contextual diversity")
}

term_fct <- c("Frequency", "Burstiness", "Context diversity",
              "Concreteness", "Babiness", "Sensorimotor", "Emotionality",
              "Length in phonemes", "Phon neighbours",
              "N features", "Form entropy", "N morphemes",
              "Subcat entropy", "MLU-w")

aoa_coefs <- aoa_models_lexcat |>
  select(language, measure, coefs) |>
  unnest(coefs) |>
  filter(Parameter != "b_Intercept") |>
  mutate(
    effect = if_else(str_detect(Parameter, ":"), "interaction", "main"),
    lexical_category = str_extract(Parameter, "lexical_category[0-9]"),
    term = if_else(effect == "interaction",
                   str_remove(Parameter, ":?lexical_category[0-9]:?"),
                   Parameter) |>
      str_replace("neighbor", "neighbour"),
    term = term |>
      factor() |>
      fct_relabel(display_predictors) |>
      fct_relevel(term_fct) |>
      fct_rev(),
    language = factor(language, levels = target_langs),
    term_cat = fct_collapse(term,
                            Morphological = c("N features", "Form entropy", "N morphemes"),
                            Syntactic = c("MLU-w", "Subcat entropy"),
                            Phonological = c("Length in phonemes", "Phon neighbours"),
                            Distributional = c("Frequency", "Burstiness", "Context diversity"),
                            Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")) |>
      fct_rev() |>
      fct_shift(-2)) |>
  rename(estimate = MAP,
         conf.low = CI_low,
         conf.high = CI_high)
                

n_by_lexcat <- aoa_predictor_data |> 
  group_by(language, lexical_category) |> 
  summarise(n = n())

n_by_lang <- n_by_lexcat |> 
  group_by(language) |> 
  summarise(n = sum(n))
```

```{r}
plot_coefs <- aoa_coefs |>
  filter(is.na(lexical_category),
         !is.na(term)) |>
  left_join(n_by_lang, by = "language") |>
  mutate(signif = ifelse(conf.low < 0 & conf.high > 0,
                         "Not significant", "Significant"),
         language = factor(language, levels = target_langs))

label_caps <- function(value) {
  value |> 
    str_to_sentence() |> 
    str_replace_all("_", " ")
}

lc_plot <- aoa_coefs |>
  select(language, measure, term, estimate, lexical_category, term_cat) |>
  pivot_wider(names_from = lexical_category, values_from = estimate) |>
  mutate(predicates = `NA` + lexical_category1,
         function_words = `NA` + lexical_category2,
         nouns = `NA` - lexical_category1 - lexical_category2) |>
  select(-c(`NA`, lexical_category1, lexical_category2)) |>
  pivot_longer(cols = c(predicates, function_words, nouns),
               names_to = "lexical_category",
               values_to = "estimate") |>
  filter(!is.na(estimate),
         !is.na(term)) |>
  left_join(n_by_lexcat, by = c("language", "lexical_category")) |>
  mutate(language = factor(language, levels = target_langs),
         lexical_category = factor(lexical_category, levels =
                                     c("nouns", "predicates", "function_words")) |>
           fct_relabel(label_caps))
```


Summary stats:
```{r}
sum_stats <- aoa_models_lexcat |> select(language, measure, stats) |> unnest(stats)
```

Variance inflation factors:
```{r}
vifs <- aoa_models |> select(language, measure, vifs) |> unnest(vifs)
```


## Cross-validation (temporarily eval=F)

```{r, eval=F}
baseline_preds <- c("freq", "concreteness", "babiness")
phon_preds <- c("length_phon", "phon_neighbors")
morph_preds <- c("form_entropy", "n_features", "n_morphemes")
syntax_preds <- c("mlu", "subcat_entropy")

pred_lists <- list(baseline_preds,
                   c(baseline_preds, phon_preds),
                   c(baseline_preds, morph_preds),
                   c(baseline_preds, syntax_preds),
                   c(baseline_preds, phon_preds, morph_preds),
                   c(baseline_preds, phon_preds, syntax_preds),
                   c(baseline_preds, morph_preds, syntax_preds),
                   c(baseline_preds, phon_preds, morph_preds, syntax_preds))

# takes ~40min
# contrasts dropped from lexical_category: some langs only have n_morphemes for predicates!?
loo_data <- aoa_predictor_data |> 
  nest(data = -c(language, measure)) |> 
  mutate(loo_models = map(data, fit_cv_models, pred_lists),
         loo_preds = map2(loo_models, data, get_cv_preds),
         cv_results = map(loo_preds, get_cv_results))
```

```{r extract_cross_validated_results, eval=F}
cv_results <- loo_data |>
  select(language, measure, cv_results) |>
  unnest(cv_results) |> 
  mutate(name = name |> factor() |> 
           fct_recode(baseline = "1", 
                      phon = "2", morph = "3", syntax = "4",
                      phon_morph = "5", phon_syntax = "6", morph_syntax = "7",
                      full = "8"))
```


## Morphological complexity
```{r morph_complexity}
# Exploratory
library(broom)
morph_complexity <- read_csv("resources/cwals.csv") |> 
  select(iso_codes, n_feat, morph_complexity = cwals_new)

ms_terms <- c("N features", "Form entropy", "N morphemes", "MLU-w") # "Subcat entropy", 

# note: uses lc_plot, which is from plots.Rmd
morph_coefs <- lc_plot |> 
  filter(term %in% ms_terms) |> 
  nest(data = -language) |> 
  mutate(iso_codes = sapply(language, convert_lang_morph_complexity)) |> 
  left_join(morph_complexity) |> 
  unnest(data) |> 
  select(-iso_codes) |> 
  mutate(term = as.factor(term))

lexcats <- c("Nouns", "Predicates", "Function words")

mc_mods <- map(c("produces", "understands"), \(y) {
  map(ms_terms, \(x) {
    map(lexcats, \(lc) {
      arm::bayesglm(estimate ~ morph_complexity, 
       data = morph_coefs |> 
         filter(term == x, measure == y, 
                lexical_category == lc))
    })
  }) |> unlist(recursive = FALSE)
}) |> unlist(recursive = FALSE)
saveRDS(mc_mods, "mc_mods.rds")

mc_vals <- expand_grid(measure = c("produces", "understands"),
                       ms_term = ms_terms,
                       lexical_category = lexcats) |> 
  mutate(mc_data = map(mc_mods, broom.mixed::tidy)) |> 
  unnest(mc_data) |> 
  mutate(ci.low = estimate - std.error,
         ci.high = estimate + std.error,
         signif = !(ci.low < 0 & ci.high > 0))
```

## All-language model
```{r, eval=F}
aoa_predictor_alllang <- aoa_predictor_data |> 
  mutate(n_morphemes = replace_na(n_morphemes, 0))

aoa_model_alllang_fix <- fit_all_lang_model(predictors, aoa_predictor_alllang,
                                            lexcat_interactions = TRUE)
saveRDS(aoa_model_alllang_fix, "aoa_model_alllang_fix.rds")
mod_all <- aoa_model_alllang_fix$model[[1]]
```

```{r, eval=F}
aoa_model_alllang_nom <- fit_all_lang_model(predictors |> setdiff("n_morphemes"), aoa_predictor_data,
                              lexcat_interactions = TRUE)
saveRDS(aoa_model_alllang_nom, "aoa_model_alllang_nom.rds")
```

```{r}
aoa_model_alllang_nom <- readRDS("aoa_model_alllang_nom.rds")
mod_all <- aoa_model_alllang_nom$model[[1]]
```

```{r}
term_fct <- c("Frequency", "Burstiness", "Context diversity", 
              "Concreteness", "Sensorimotor", "Babiness", "Emotionality",
              "Phon neighbours", "Length in phonemes",
              "Form entropy", "N features",
              "Subcat entropy", "MLU-w")
```


```{r}
library(broom.mixed)
library(tidybayes)
library(bayestestR)
mod_all_outputs <- tidy(mod_all)

all_coefs <- mod_all_outputs |> 
  filter(term != "Intercept") |>
  mutate(
    effect = if_else(str_detect(term, ":"), "interaction", "main"),
    lexical_category = str_extract(term, "lexical_category[0-9]"),
    type = case_when(
      str_detect(term, "sd_") ~ "random",
      str_detect(term, "cor_") ~ "correlation",
      TRUE ~ "fixed"
    ),
    term = if_else(effect == "interaction",
                   str_remove(term, ":?lexical_category[0-9]:?"),
                   term) |>
      str_replace("neighbor", "neighbour") |> 
      str_remove("sd__") |> 
      str_remove("cor__"),
    term = term |>
      factor() |>
      fct_relabel(display_predictors) |>
      fct_relevel(term_fct) |>
      fct_rev(),
    term_cat = fct_collapse(term,
                            Morphological = c("N features", "Form entropy", "N morphemes"),
                            Syntactic = c("MLU-w", "Subcat entropy"),
                            Phonological = c("Length in phonemes", "Phon neighbours"),
                            Distributional = c("Frequency", "Burstiness", "Context diversity"),
                            Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")) |>
      fct_rev() |>
      fct_shift(-2)) |> 
  filter(type != "correlation")

all_draws <- gather_draws(mod_all, `b_.*`, `r_.*`, regex=T) |> 
  separate_wider_delim(.variable,
                       names = c("variable", "language", "measure"),
                       delim = regex("[\\[\\],]"),
                       too_few = "align_start",
                       too_many = "drop")
all_draws_fixed <- all_draws |> 
  filter(str_starts(variable, "b_")) |> 
  mutate(variable = str_remove(variable, "b_"))
all_draws_random <- all_draws |>
  filter(str_starts(variable, "r_"))

all_draws_est <- all_draws_random |> 
  left_join(all_draws_fixed |> select(-language, -measure), 
            by = join_by(.chain, .iteration, .draw, measure == variable)) |> 
  mutate(estimate = .value.x + .value.y)
```

```{r}
all_langs_est <- all_draws_est |> 
  group_by(language, measure) |> 
  summarise(map = map_estimate(estimate)$MAP_Estimate,
            eap = mean(estimate),
            sd = sd(estimate),
            hdi = hdi(estimate),
            eti = eti(estimate),
            pct_rope = sum(-.1 <= estimate & estimate <= .1) / n()) |> 
  mutate(hdi.lower = hdi$CI_low,
         hdi.upper = hdi$CI_high,
         eti.lower = eti$CI_low,
         eti.upper = eti$CI_high,
         reliability = sign(hdi.lower) == sign(hdi.upper)) |>
  select(-hdi, -eti)
all_fixed_est <- all_draws_fixed |> 
  group_by(variable) |> 
  rename(estimate = .value) |> 
  summarise(map = map_estimate(estimate)$MAP_Estimate,
            eap = mean(estimate),
            sd = sd(estimate),
            hdi = hdi(estimate),
            eti = eti(estimate),
            pct_rope = sum(-.1 <= estimate & estimate <= .1) / n()) |> 
  mutate(hdi.lower = hdi$CI_low,
         hdi.upper = hdi$CI_high,
         eti.lower = eti$CI_low,
         eti.upper = eti$CI_high,
         reliability = sign(hdi.lower) == sign(hdi.upper)) |>
  select(-hdi, -eti)
```

```{r}
plot_all_langs <- all_langs_est |> 
  filter(!str_detect(measure, "lexical_category"),
         measure != "Intercept") |> 
  rename(term = measure) |> 
  mutate(language = str_replace_all(language, "\\.", " "),
         term = term |>
           str_replace("neighbor", "neighbour") |>
           factor() |>
           fct_relabel(display_predictors) |>
           fct_relevel(term_fct) |>
           fct_rev(),
         language = factor(language, levels = target_langs),
         term_cat = fct_collapse(term,
                                 Morphological = c("N features", "Form entropy", "N morphemes"),
                                 Syntactic = c("MLU-w", "Subcat entropy"),
                                 Phonological = c("Length in phonemes", "Phon neighbours"),
                                 Distributional = c("Frequency", "Burstiness", "Context diversity"),
                                 Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")),
         reliability = ifelse(reliability, "Reliable", "Not reliable"))
plot_fixed <- all_fixed_est |> 
  filter(!str_detect(variable, "lexical_category"),
         variable != "Intercept") |> 
  rename(term = variable) |> 
  mutate(term = term |>
           str_replace("neighbor", "neighbour") |>
           factor() |>
           fct_relabel(display_predictors) |>
           fct_relevel(term_fct) |>
           fct_rev(),
         term_cat = fct_collapse(term,
                                 Morphological = c("N features", "Form entropy", "N morphemes"),
                                 Syntactic = c("MLU-w", "Subcat entropy"),
                                 Phonological = c("Length in phonemes", "Phon neighbours"),
                                 Distributional = c("Frequency", "Burstiness", "Context diversity"),
                                 Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")))

ggplot(plot_all_langs,
       aes(x = map, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_point(aes(col = language, shape = reliability), 
             alpha = .7, size = 2) +
  geom_crossbar(aes(xmin = map, xmax = map), 
                width = 0.5, fatten = 2,
                data = plot_fixed) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", color = "Language") +
  theme_mikabr() +
  coord_cartesian(xlim = c(-2.5, 2.5)) +
  scale_shape_manual(values = c(21, 16))
```

Coefficient of variation
```{r}
coef_var <- all_draws_est |> 
  group_by(.chain, .iteration, .draw, measure) |> 
  summarise(mean = mean(.value.y),
            sd = sd(estimate)) |> 
  mutate(coef_of_var = sd / abs(mean))
coef_var_est <- coef_var |> 
  group_by(measure) |> 
  summarise(map = map_estimate(coef_of_var, precision = 2^20)$MAP_Estimate,
            eap = mean(coef_of_var),
            sd = sd(coef_of_var),
            hdi = hdi(coef_of_var),
            eti = eti(coef_of_var),
            pct_rope = sum(-.1 <= coef_of_var & coef_of_var <= .1) / n()) |> 
  mutate(hdi.lower = hdi$CI_low,
         hdi.upper = hdi$CI_high,
         eti.lower = eti$CI_low,
         eti.upper = eti$CI_high,
         reliability = sign(hdi.lower) == sign(hdi.upper)) |>
  select(-hdi, -eti)
```


```{r}
plot_coef_var <- coef_var_est |> 
  rename(variable = measure) |> 
  filter(!str_detect(variable, "lexical_category"),
         variable != "Intercept") |> 
  rename(term = variable) |> 
  mutate(term = term |>
           str_replace("neighbor", "neighbour") |>
           factor() |>
           fct_relabel(display_predictors) |>
           fct_relevel(term_fct) |>
           fct_rev(),
         term_cat = fct_collapse(term,
                                 Morphological = c("N features", "Form entropy", "N morphemes"),
                                 Syntactic = c("MLU-w", "Subcat entropy"),
                                 Phonological = c("Length in phonemes", "Phon neighbours"),
                                 Distributional = c("Frequency", "Burstiness", "Context diversity"),
                                 Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")))

ggplot(plot_coef_var,
       aes(x = map, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_pointrange(aes(xmin = hdi.lower, xmax = hdi.upper)) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  labs(x = "Coefficient of variation", y = "") +
  theme_mikabr() +
  coord_cartesian(xlim = c(0, 10))
```

Lex cat plots
```{r}
all_langs_lexcat_est <- all_draws_est |> 
  mutate(lexcat = str_extract(measure, "lexical_category[0-9]") |> 
           replace_na("main"),
         measure = str_remove(measure, ":?lexical_category[0-9]:?"),
         measure = ifelse(measure == "", "Intercept", measure)) |> 
  select(-.value.x, -.value.y) |>
  pivot_wider(names_from = lexcat, values_from = estimate) |> 
  mutate(nouns = main - lexical_category1 - lexical_category2,
         predicates = main + lexical_category1,
         function_words = main + lexical_category2) |> 
  select(-main, -lexical_category1, -lexical_category2) |> 
  pivot_longer(cols = c(nouns, predicates, function_words),
               names_to = "lexical_category",
               values_to = "estimate") |> 
  group_by(language, measure, lexical_category) |> 
  summarise(map = map_estimate(estimate)$MAP_Estimate,
            eap = mean(estimate),
            sd = sd(estimate),
            hdi = hdi(estimate),
            eti = eti(estimate),
            pct_rope = sum(-.1 <= estimate & estimate <= .1) / n()) |> 
  mutate(hdi.lower = hdi$CI_low,
         hdi.upper = hdi$CI_high,
         eti.lower = eti$CI_low,
         eti.upper = eti$CI_high,
         reliability = sign(hdi.lower) == sign(hdi.upper)) |>
  select(-hdi, -eti)

all_fixed_lexcat_est <- all_draws_fixed |> 
  mutate(measure = variable,
         lexcat = str_extract(measure, "lexical_category[0-9]") |> 
           replace_na("main"),
         measure = str_remove(measure, ":?lexical_category[0-9]:?"),
         measure = ifelse(measure == "", "Intercept", measure)) |> 
  select(-variable) |> 
  rename(estimate = .value) |>
  pivot_wider(names_from = lexcat, values_from = estimate) |> 
  mutate(nouns = main - lexical_category1 - lexical_category2,
         predicates = main + lexical_category1,
         function_words = main + lexical_category2) |> 
  select(-main, -lexical_category1, -lexical_category2) |> 
  pivot_longer(cols = c(nouns, predicates, function_words),
               names_to = "lexical_category",
               values_to = "estimate") |> 
  group_by(measure, lexical_category) |> 
  summarise(map = map_estimate(estimate)$MAP_Estimate,
            eap = mean(estimate),
            sd = sd(estimate),
            hdi = hdi(estimate),
            eti = eti(estimate),
            pct_rope = sum(-.1 <= estimate & estimate <= .1) / n()) |> 
  mutate(hdi.lower = hdi$CI_low,
         hdi.upper = hdi$CI_high,
         eti.lower = eti$CI_low,
         eti.upper = eti$CI_high,
         reliability = sign(hdi.lower) == sign(hdi.upper)) |>
  select(-hdi, -eti)

plot_all_langs_lexcat <- all_langs_lexcat_est |> 
  filter(measure != "Intercept") |> 
  rename(term = measure) |> 
  mutate(language = str_replace_all(language, "\\.", " "),
         term = term |>
           str_replace("neighbor", "neighbour") |>
           factor() |>
           fct_relabel(display_predictors) |>
           fct_relevel(term_fct) |>
           fct_rev(),
         language = factor(language, levels = target_langs),
         term_cat = fct_collapse(term,
                                 Morphological = c("N features", "Form entropy", "N morphemes"),
                                 Syntactic = c("MLU-w", "Subcat entropy"),
                                 Phonological = c("Length in phonemes", "Phon neighbours"),
                                 Distributional = c("Frequency", "Burstiness", "Context diversity"),
                                 Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")),
         reliability = ifelse(reliability, "Reliable", "Not reliable"),
         lexical_category = lexical_category |> 
           factor(levels = c("nouns", "predicates", "function_words")) |> 
           fct_relabel(\(x) {
             x |> 
               str_to_sentence() |> 
               str_replace_all("_", " ")
           }))

plot_all_fixed_lexcat <- all_fixed_lexcat_est |> 
  filter(measure != "Intercept") |> 
  rename(term = measure) |> 
  ungroup() |> 
  mutate(term = term |>
           str_replace("neighbor", "neighbour") |>
           factor() |>
           fct_relabel(display_predictors) |>
           fct_relevel(term_fct) |>
           fct_rev(),
         term_cat = fct_collapse(term,
                                 Morphological = c("N features", "Form entropy", "N morphemes"),
                                 Syntactic = c("MLU-w", "Subcat entropy"),
                                 Phonological = c("Length in phonemes", "Phon neighbours"),
                                 Distributional = c("Frequency", "Burstiness", "Context diversity"),
                                 Semantic = c("Concreteness", "Babiness", "Sensorimotor", "Emotionality")),
         reliability = ifelse(reliability, "Reliable", "Not reliable"),
         lexical_category = lexical_category |> 
           factor(levels = c("nouns", "predicates", "function_words")) |> 
           fct_relabel(\(x) {
             x |> 
               str_to_sentence() |> 
               str_replace_all("_", " ")
           }))

ggplot(plot_all_langs_lexcat,
       aes(x = map, y = term)) +
  facet_grid(term_cat ~ lexical_category, scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_point(aes(col = language, shape = reliability), alpha = .7) +
  geom_crossbar(aes(xmin = map, xmax = map), 
                width = 0.5, fatten = 2,
                data = plot_all_fixed_lexcat) +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", color = "Language") +
  theme_mikabr() +
  coord_cartesian(xlim = c(-3.5, 3.5)) +
  scale_shape_manual(values = c(21, 16)) +
  theme(legend.position = "none")
```

```{r}
plot_all_fixed_lexcat |> 
  arrange(lexical_category, term_cat, term) |> 
  ggplot(aes(x = map, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_rect(aes(xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax = Inf), 
            fill = "#e0e0e0", alpha = 0.2) +
  geom_point(aes(shape = reliability, col = lexical_category), size = 2.5) +
  geom_path(aes(group = lexical_category, col = lexical_category), position = "identity") +
  geom_vline(xintercept = 0, color = "#606060", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Reliability", col = "Lexical category") +
  theme_mikabr() +
  coord_cartesian(xlim = c(-2, 2)) +
  scale_shape_manual(values = c(21, 16))
```

## XGBoost
```{r}
library(xgboost)

aoa_pred_data_xgb <- aoa_predictor_data |> 
  select(language, lexical_category, all_of(predictors)) |> 
  mutate(across(all_of(predictors), as.numeric),
         lexical_category = as.integer(lexical_category),
         language = language |> factor() |> as.integer()) |> 
  as.matrix()
aoa_pred_data_xgb_df <- aoa_predictor_data |> 
  select(language, lexical_category, all_of(predictors)) |> 
  mutate(across(all_of(predictors), as.numeric),
         language = language |> factor())
aoa_out_data_xgb <- aoa_predictor_data |> 
  pull(aoa)
```


```{r eval=F}
hyper_grid <- expand.grid(
  eta = 0.1,
  max_depth = 3:6, 
  min_child_weight = 3,
  subsample = 0.5, 
  colsample_bytree = 0.5,
  gamma = c(0, 1, 10, 100, 1000),
  lambda = c(0, 1e-2, 0.1, 1, 10, 100),
  alpha = c(0, 1e-2, 0.1, 1, 10, 100, 1000),
  rmse = 0,          # a place to dump RMSE results
  trees = 0          # a place to dump required number of trees
)

aoa_dtrain <- xgb.DMatrix(data = aoa_pred_data_xgb, label = aoa_out_data_xgb)
# aoa_xgb_model <- xgboost(data = aoa_dtrain, 
#                          nrounds = 1000, 
#                          max_depth = 6, 
#                          eta = 0.1, 
#                          objective = "reg:squarederror", 
#                          eval_metric = "rmse",
#                          verbose = 1,
#                          early_stopping_rounds = 50)
# min(aoa_xgb_model$evaluation_log$train_rmse)

# aoa_xgb_cv <- xgb.cv(data = aoa_dtrain, 
#                             nrounds = 1000, 
#                             max_depth = 6, 
#                             eta = 0.1, 
#                             objective = "reg:squarederror", 
#                             eval_metric = "rmse",
#                             verbose = 1,
#                             early_stopping_rounds = 50,
#                             nfold = 10)
# min(aoa_xgb_cv$evaluation_log$test_rmse_mean)

for (i in seq_len(nrow(hyper_grid))) {
  set.seed(123)
  message("Fitting model ", i, " of ", nrow(hyper_grid))
  params <- hyper_grid[i, ]
  aoa_xgb_cv <- xgb.cv(data = aoa_dtrain, 
                       nrounds = 1000, 
                       max_depth = params$max_depth, 
                       eta = params$eta, 
                       min_child_weight = params$min_child_weight,
                       subsample = params$subsample, 
                       colsample_bytree = params$colsample_bytree,
                       gamma = params$gamma,
                       lambda = params$lambda,
                       alpha = params$alpha,
                       objective = "reg:squarederror", 
                       eval_metric = "rmse",
                       verbose = FALSE,
                       early_stopping_rounds = 50,
                       nfold = 5)
  hyper_grid$rmse[i] <- min(aoa_xgb_cv$evaluation_log$test_rmse_mean)
  hyper_grid$trees[i] <- aoa_xgb_cv$best_iteration
}
```

```{r}
library(shapviz)

best_xgb_params <- list(
  learning_rate = 0.1,
  max_depth = 5, 
  min_child_weight = 3,
  subsample = 0.5, 
  colsample_bytree = 0.5,
  min_split_loss = 100,
  reg_lambda = 1,
  reg_alpha = 100,
  objective = "reg:squarederror",
  eval_metric = "rmse"
)
```

```{r eval=F}
# doesn't work, too few data points
aoa_nested <- aoa_predictor_data |> 
  select(language, lexical_category, aoa, all_of(predictors)) |> 
  mutate(lexical_category = lexical_category |> factor() |> as.numeric()) |> 
  group_by(language) |> 
  nest(aoas = aoa,
       predictors = all_of(c("lexical_category", predictors))) |> 
  mutate(dmat = map2(predictors, aoas, 
                     ~ xgb.DMatrix(data = as.matrix(.x), label = .y$aoa)),
         model = map(dmat, ~ xgb.train(data = .x, 
                                       nrounds = 1000,
                                       params = best_xgb_params)),
         shap = map2(model, predictors, ~ shapviz(.x,
                                                  X_pred = data.matrix(.y),
                                                  interaction = TRUE)))
```


```{r}
aoa_pred_dmat <- xgb.DMatrix(data = aoa_pred_data_xgb_df, label = aoa_out_data_xgb)

# aoa_xgb_model <- xgboost(x = aoa_pred_data_xgb_df,
#                          y = aoa_out_data_xgb,
#                          nrounds = 1000,
#                          max_depth = best_xgb_params$max_depth, 
#                          learning_rate = best_xgb_params$eta, 
#                          min_child_weight = best_xgb_params$min_child_weight,
#                          subsample = best_xgb_params$subsample, 
#                          colsample_bytree = best_xgb_params$colsample_bytree,
#                          min_split_loss = best_xgb_params$gamma,
#                          reg_lambda = best_xgb_params$lambda,
#                          reg_alpha = best_xgb_params$alpha,
#                          objective = "reg:squarederror", 
#                          eval_metric = "rmse")

aoa_xgb_model <- xgb.train(data = aoa_pred_dmat,
                           nrounds = 1000,
                           params = best_xgb_params)

shap <- shapviz(aoa_xgb_model,
                X_pred = data.matrix(aoa_pred_data_xgb_df),
                interaction = TRUE)

aoa_imp <- sv_importance(shap, max_display = 20)
aoa_bee <- sv_importance(shap, kind = "bee", max_display = 20)
```


```{r eval=F}
best_xgb_params <- hyper_grid |> 
  filter(rmse == min(rmse)) |> 
  select(-rmse, -trees)

aoa_xgb_model <- xgboost(data = aoa_dtrain, 
                         nrounds = 1000,
                         max_depth = best_xgb_params$max_depth, 
                         eta = best_xgb_params$eta, 
                         min_child_weight = best_xgb_params$min_child_weight,
                         subsample = best_xgb_params$subsample, 
                         colsample_bytree = best_xgb_params$colsample_bytree,
                         gamma = best_xgb_params$gamma,
                         lambda = best_xgb_params$lambda,
                         alpha = best_xgb_params$alpha,
                         objective = "reg:squarederror", 
                         eval_metric = "rmse",
                         verbose = TRUE)
```


Everything above here has been verified. 


Temporary: plots
```{r}
theme_mikabr <- function(base_size = 14, base_family = "Open Sans") {
  ggplot2::`%+replace%`(
    ggplot2::theme_bw(base_size = base_size, base_family = base_family),
    ggplot2::theme(panel.grid = ggplot2::element_blank(),
                   strip.background = ggplot2::element_blank(),
                   legend.key = ggplot2::element_blank())
  )
}
```


```{r}
ggplot(plot_coefs |> filter(!is.na(estimate), !is.na(term), term != "(Intercept)", is.na(group)) |> 
         mutate(language = factor(language, levels = target_langs),
                term_cat = fct_collapse(term,
                                        Morphological = c("N features", "Form entropy", "N morphemes"),
                                        Syntactic = c("MLU-w", "Subcat entropy"),
                                        Phonological = c("Length in phonemes", "Phon neighbors"),
                                        Other = c("Frequency", "Contextual diversity", 
                                                  "Concreteness", "Babiness")) |> 
                  fct_rev() |> 
                  fct_shift(-2)) |> 
         filter(measure == "production"), 
       aes(x = estimate, y = term)) +
  facet_grid(term_cat ~ ., scales = "free", space = "free") +
  geom_point(aes(shape = signif, color = language, size = n),  alpha = 0.7) +
  scale_shape_manual(values = c(21, 16)) +
  stat_summary(geom = "crossbar", fun = median, fun.min = median,
               fun.max = median, fatten = 2, width = 0.5) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "", 
       shape = "Significance", color = "Language")+
  theme(legend.position="none") +
  theme_mikabr() +
  coord_cartesian(xlim = c(-2.5, 2.5))
```

```{r}
ggplot(lc_plot |> 
         mutate(language = factor(language, levels = target_langs),
                lexical_category = factor(lexical_category, levels = 
                                            c("nouns", "predicates", "function_words")) |> 
                  fct_relabel(label_caps),
                term_cat = fct_collapse(term,
                                        Morphological = c("N features", "Form entropy", "N morphemes"),
                                        Syntactic = c("MLU-w", "Subcat entropy"),
                                        Phonological = c("Length in phonemes", "Phon neighbors"),
                                        Other = c("Frequency", "Contextual diversity", 
                                                  "Concreteness", "Babiness")) |> 
                  fct_rev() |> 
                  fct_shift(-2),
                term = term |> fct_relevel("Babiness", "Concreteness", "Frequency")) |> 
         filter(measure == "production"), 
       aes(x = estimate, y = term)) +
  facet_grid(term_cat ~ lexical_category, scales = "free", space = "free") +
  geom_point(aes(color = language, size = n),  alpha = 0.7) +
  # scale_shape_manual(values = c(16, 21)) +
  stat_summary(geom = "crossbar", fun = median, fun.min = median,
               fun.max = median, fatten = 2, width = 0.5) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dotted") +
  labs(x = "Coefficient estimate", y = "") +
  theme_mikabr() +
  theme(legend.position = "none") +
  coord_cartesian(xlim = c(-3.5, 3.5))
```

```{r correlo-dendrogram}
dd_coefs <- aoa_coefs |> 
  filter(# !str_detect(term, "lexical_category"),
         is.na(lexical_category), 
         term != "sd__Observation") |> 
  select(language, measure, term, lexical_category, estimate) |> 
  filter(measure == "produces") |> 
  pivot_wider(names_from = c(term, lexical_category),
              values_from = estimate) |> 
  select(-measure)

dd_matrix <- dd_coefs |> 
  select(-language) |> 
  as.matrix() |> 
  `rownames<-`(dd_coefs$language)

COR_SCALE <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

GERMANIC <- "#cc0000"
ROMANCE <- "#e69138"
SLAVIC <- "#f1c232"
JAPONIC <- "#8db63d"
KOREANIC <- "#47ad44"
SEMITIC <- "#45816e"
SINOTIBETAN <- "#3d85c6"
TURKIC <- "#3d50c6"
URALIC <- "#674ea7"

lang_cols <- c(# SEMITIC, 
               SINOTIBETAN, ROMANCE, SLAVIC,
               SLAVIC, GERMANIC, GERMANIC, GERMANIC,
               GERMANIC, GERMANIC, URALIC, ROMANCE, 
               ROMANCE, GERMANIC, SEMITIC, URALIC, 
               ROMANCE, KOREANIC, SINOTIBETAN, 
               SINOTIBETAN, GERMANIC, ROMANCE, SLAVIC, 
               ROMANCE, ROMANCE, GERMANIC, TURKIC, JAPONIC)

dd_heatmap <- gplots::heatmap.2(cor(t(dd_matrix), use = "pairwise.complete.obs"),
                        dendrogram = "column",
                        trace = "none",
                        col = COR_SCALE(30),
                        colRow = lang_cols,
                        colCol = lang_cols,
                        mar = c(10, 10))
```





```{r}
cv_plot <- cv_results |> 
  filter(measure == "produces") |> 
  select(language, name, mean_abs_dev, ci_mad) |> 
  pivot_wider(names_from = name,
              values_from = c(mean_abs_dev, ci_mad)) |> 
  mutate(across(starts_with("mean_abs_dev_"), \(v) {v - mean_abs_dev_baseline})) |> 
  pivot_longer(cols = -language,
               names_to = c(".value", "name"),
               names_pattern = "(mean_abs_dev|ci_mad)_(.*)") |> 
  mutate(Model = name |> 
           fct_relevel("phon", "morph", "syntax",
                       "phon_morph", "phon_syntax", "morph_syntax",
                       "full") |> 
           fct_relabel(\(v) str_replace_all(v, "_", "+")))

ggplot(cv_plot |> filter(name != "baseline"), 
       aes(x = mean_abs_dev, y = language, col = Model)) +
  geom_point() +
  geom_vline(xintercept = 0, color = "grey", lty = "dotted") +
  labs(x = "Mean absolute deviation (mo)", y = "Language") +
  theme_mikabr()
```


```{r}
mlu_pred <- morph_coefs |> 
  filter(# measure == "production",
         term == "MLU-w",
         lexical_category == "Predicates")
ggplot(mlu_pred, aes(x = morph_complexity, y = estimate)) +
  geom_point(aes(col = language)) + 
  geom_smooth(method = "lm", col = "black") +
  geom_hline(yintercept = 0, color = "grey", lty = "dotted") +
  geom_label_repel(aes(label = language, col = language), size = 2) +
  labs(x = "Estimated morphological complexity", 
       y = "Coefficient estimate",
       col = "Language") +
  theme_mikabr() +
  theme(legend.position = "none")
```











```{r all_lang_model}
library(broom.mixed)
# aoa_all_lang_model <- fit_all_lang_model(predictors[predictors != "length_char"], 
#                                          aoa_predictor_data,
#                                          lexcat_interactions = FALSE)
aoa_all_lang_model_2 <- fit_all_lang_model(predictors[predictors != "length_char"], 
                                         aoa_predictor_data,
                                         lexcat_interactions = FALSE)
aoa_all_lang_model_2b <- fit_all_lang_model(predictors[predictors != "length_char"], 
                                         aoa_predictor_data,
                                         lexcat_interactions = TRUE)
aoa_all_lang_model_3 <- fit_all_lang_model(predictors[predictors != "length_char"], 
                                         aoa_predictor_data,
                                         morphcomp_interactions = TRUE,
                                         lexcat_interactions = FALSE)
aoa_all_lang_model_3b <- fit_all_lang_model(predictors[predictors != "length_char"], 
                                         aoa_predictor_data,
                                         morphcomp_interactions = TRUE,
                                         lexcat_interactions = TRUE)
# coefs_comp <- aoa_all_lang_model |> select(measure, coefs) |> unnest(coefs) 
coefs_comp_2 <- aoa_all_lang_model_2 |> select(measure, coefs) |> unnest(coefs) 
coefs_comp_2b <- aoa_all_lang_model_2b |> select(measure, coefs) |> unnest(coefs) 
coefs_comp_3 <- aoa_all_lang_model_3 |> select(measure, coefs) |> unnest(coefs)
coefs_comp_3b <- aoa_all_lang_model_3b |> select(measure, coefs) |> unnest(coefs)
# coefs_comp <- aoa_complexity_models |> select(language, measure, coefs) |> unnest(coefs) 

predictors_old <- c("freq", "concreteness", "babiness", "length_phon", "mlu")
aoa_all_lang_model_old <- fit_all_lang_model(predictors_old, 
                                             aoa_predictor_data,
                                             lexcat_interactions = TRUE)
# aoa_all_lang_model_old <- fit_all_lang_model(predictors_old, 
#                                              aoa_predictor_data,
#                                              lexcat_interactions = TRUE)
coefs_comp_old <- aoa_all_lang_model_old |> select(measure, coefs) |> unnest(coefs)
```



```{r save_worst_produced_data, eval = FALSE}
worst_predicted_unilemmas<- function(lang, meas, loo_preds){ loo_preds |>
  unnest(cols = c(loo_preds))|>
  filter(language == lang, measure == meas) |>
  arrange(desc(abs_dev)) |>
  head(50)
}
worst_uni_produce<-map_df(target_langs, worst_predicted_unilemmas, "produces", loo_preds) %>% 
  group_by(test_word) %>%
  summarise(count_lang=n(),
  lang_names = paste0(language, collapse = ","),
  aoa_mean=mean(aoa),
  aoa_pred_mean=mean(aoa_pred))
worst_uni_produce1<-loo_preds |>
  unnest(cols = c(loo_preds))|>
  filter(measure == "produces") |>
  filter(abs_dev>5)|>
  arrange(desc(abs_dev))
saveRDS(worst_uni_produce, "data/plots/worst_uni_produce.rds" )
```
