---
title: "AoA prediction template"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(dplyr.summarise.inform = FALSE)

# load libraries
library(tidyverse)
library(glue)
library(wordbankr)
library(childesr)
library(broom)
library(jglmm)
library(modelr)

# load functions
walk(list.files("scripts", pattern = "*.R$", full.names = TRUE), source)
```

This template provides the structure for how to fit age of acquisition (AoA) prediction models, using data and scripts in this repository.

The general steps are:
- loading the provided CDI data and predictor data
- adding your predictor(s) to the provided predictor data
- using the functions in `scripts/prep_data.R` to prepare the data for modeling
- using the functions in `scripts/fit_models.R` to fit models and extract information from them


# Wordbank data

Loading cached Wordbank data for English:
```{r}
eng_wb_data <- readRDS("data/wordbank/english_(american).rds")
eng_wb_data
```

Loading cached Wordbank data for multiple languages:
```{r}
# target_langs <- c("Croatian", "Danish", "English (American)",
#                   "French (Quebecois)", "Italian", "Norwegian", "Russian",
#                   "Spanish (Mexican)", "Swedish", "Turkish")
target_langs <- c("English (American)")

wb_data <- map_df(target_langs, function(lang) {
  message(glue("Loading data for {lang}..."))
  norm_lang <- normalize_language(lang)
  readRDS(glue("data/wordbank/{norm_lang}.rds"))
})
```

Creating saved Wordbank data for English:
```{r, eval=FALSE}
create_wb_data("English (American)")
```

Creating saved Wordbank data for many languages:
```{r, eval=FALSE}
walk(target_langs, create_wb_data)
```

Creating saved Wordbank data one step at a time (potentially making changes between steps):
```{r, eval=FALSE}
eng_wg <- create_inst_data("English (American)", "WG")
eng_ws <- create_inst_data("English (American)", "WS")
eng_wg_summary <- collapse_inst_data(eng_wg)
eng_ws_summary <- collapse_inst_data(eng_ws)
eng_comb_summary <- combine_form_data(list(eng_wg_summary, eng_ws_summary))
```


# Predictors

Merge in the by-concept predictors (babiness, concreteness, etc) to the unilemmas and the by word predictors (phonemes) to the words/definitions.

```{r}
uni_lemmas <- get_uni_lemmas(wb_data)

babiness_map <- c(word = "word", babiness = "babyAVG")
babiness <- uni_lemmas |> map_predictor("babiness", babiness_map)

valence_map <- c(word = "Word", valence = "V.Mean.Sum", arousal = "A.Mean.Sum")
valence <- uni_lemmas |> map_predictor("valence", valence_map)

concreteness_map <- c(word = "Word", concreteness = "Conc.M")
concreteness <- uni_lemmas |> map_predictor("concreteness", concreteness_map)
```

```{r, eval=FALSE}
# TODO: requires espeak
# http://espeak.sourceforge.net

phonemes <- uni_lemmas |> map_phonemes()
# left_join(phonemes, by = c("language", "uni_lemma")) |>
```

Loading cached CHILDES data for English:
```{r}
eng_childes <- readRDS("data/childes/uni_metrics_english_(american).rds")
eng_childes
```

Loading cached CHILDES data for multiple languages:
```{r}
uni_lemma_map <- build_uni_lemma_map(uni_lemmas)
target_langs <- c("English (American)")

childes_metrics <- map_df(target_langs, function(lang) {
  message(glue("Loading CHILDES data for {lang}..."))
  norm_lang <- normalize_language(lang)
  readRDS(glue("data/childes/uni_metrics_{norm_lang}.rds"))
})
```

Creating saved CHILDES data for English, potentially changing which metrics are computed and/or arguments that are passed to `childesr`:
```{r, eval=FALSE}
metric_funs <- list(compute_count, compute_mlu, compute_positions,
                    compute_length_char, compute_length_phon)
corpus_args <- list(corpus = NULL, role = NULL, role_exclude = "Target_Child",
                    age = NULL, sex = NULL, part_of_speech = NULL, token = "*")

eng_token_metrics <- get_childes_metrics("English (American)", metric_funs,
                                         corpus_args)
eng_uni_lemma_metrics <- get_uni_lemma_metrics("English (American)",
                                               uni_lemma_map)
```

Creating saved CHILDES data for many languages:
```{r, eval=FALSE}
walk(target_langs, get_childes_metrics)
walk(target_langs, get_uni_lemma_metrics, uni_lemmas)
```

Combine mapped predictors and CHILDES predictors:
```{r}
uni_joined <- uni_lemmas |>
  left_join(babiness, by = c("language", "uni_lemma")) |>
  left_join(valence, by = c("language", "uni_lemma")) |>
  left_join(concreteness, by = c("language", "uni_lemma")) |>
  left_join(childes_metrics, by = c("language", "uni_lemma"))
```


Residualize solo freq and final freq

```{r}
```

```{r impute}
prepped_data <- uni_joined |>
  # select out just the by lexical item data
  unnest(cols = "items") |>
  # select(-c(age, num_true, total, form, item_id)) |>
  distinct() |>
  # pull out categories from classes
  mutate(lexical_category = if_else(str_detect(lexical_class, ","), "other",
                                    lexical_class),
         # collapse v, adj, adv into one category
         lexical_category = lexical_category |> as_factor() |>
           suppressWarnings(
             fct_collapse("predicates" = c("verbs", "adjectives", "adverbs"))
             )) |>
  select(-lexical_class)

pred_sources <- list(
  # c("frequency", "MLU", "final_frequency", "solo_frequency"),
  c("valence", "arousal"),
  "concreteness", "babiness"#, "num_phons"
)

imputed_data <- prepped_data |> do_full_imputation(pred_sources, 20)
```


# Model fitting

aoa lm model:
```{r aoa-lm}
wb_data <- wb_data |>
  mutate(num_false = total - num_true,
         prop = num_true / total) |>
  select(language, measure, uni_lemma, age, prop, num_true, num_false, total, items)

aoas <- wb_data |>
  group_by(language, measure) |>
  nest() |>
  mutate(aoa = map(data, get_aoas, max_steps = 400)) |>
  select(-data) |>
  unnest(cols = c(aoa))

word_values <- aoas |>
  left_join(imputed_data |>
              select(-data) |>
              unnest(cols = c(imputed)), 
            by = c("language", "uni_lemma"))

joined_data <- wb_data |>
  left_join(word_values, by = c("language", "measure", "uni_lemma"))

predictors <- pred_sources |> unlist()

fitted_aoa_models <- fit_models(joined_data, predictors, full = FALSE)
```

age glmer model:
```{r age-glmer}
## TODO: fix fit_models; currently failing in Julia
fitted_age_models <- fit_models(joined_data, predictors, full = TRUE)
```

Cross-validation:
```{r}
loo_df <- crossv_loo(ungroup(word_values))
loo_models <- fit_cv_models(word_values, list(make_effs_formula(predictors, FALSE, TRUE)), loo_df)
loo_preds <- get_cv_preds(loo_models, word_values)
cv_results <- get_cv_results(loo_preds)
```

