---
title: "surprisal_frequency_data_wrangling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tools)
library(corrplot)
library(tidyverse)
library(glue)
```

Get combined unique clean word lists for frequency count script per language (no need to run this again)
```{r unique_words, eval=FALSE}
combine_clean_word_lists <- function(lang){
  lang_path <- glue("./surprisals/word-lists/{lang}/")
  name <- glue("./surprisals/word-lists/{lang}/unique_clean_words.csv")
  files = list.files(path=lang_path, pattern="*.csv", full.names=TRUE, recursive=FALSE)
  lang_data <- files |> map(read_csv) |> reduce(rbind)
  clean_words <- lang_data |> select(word_clean) |> unique()
  write.csv(clean_words, file=name)
  return(clean_words)
}
combine_clean_word_lists_by_lang("eng")
```


load in surprisal results for all runs to verify correlations
```{r surprisals}

my_get_run <- function(file){
  file_name = strsplit(file_path_sans_ext(file), "/")[[1]]
  file_name = file_name[(length(file_name))]
  run_num = str_sub(file_name, -1, -1)
  surprisal_name = paste("avg_surprisal", run_num, sep="_")
  perplexity_name = paste("avg_perplexity", run_num, sep="_")
  data <- read_csv(file)
  names(data)[names(data) == "avg_surprisal"] <- surprisal_name
  names(data)[names(data) == "avg_perplexity"] <- perplexity_name
  return(data)
}

get_all_runs_surprisal <- function(lang){
  lang_path <- glue("./surprisals/lstm-surprisals/{lang}/")
  files = list.files(path=lang_path, pattern="*.csv", full.names=TRUE, recursive=FALSE)
  lang_data <- files |> map(my_get_run) |> reduce(left_join)
  return(lang_data)
}

target_langs = c("English (American)", "English (British)", "Spanish (Mexican)", "Spanish (European)", "German", "Mandarin (Beijing)", "Mandarin (Taiwanese)", "French (Quebecois)")

all_surprisals <- map(target_langs, get_all_runs_surprisal) |> reduce(rbind)
all_surprisals$language |> unique()


```

get the correlation across models for each language surprisal set 

```{r cor, eval=FALSE}

my_get_cor_plot <- function(data){
  selected_data <- data |> select(-c(word_clean, n_tokens, n_instances, language))
  M = cor(selected_data, method = "pearson", use = "complete.obs")
  print(M)
  corrplot(M, method = 'number')
}

all_surprisals |> group_by(language) |> 
  group_split() |>
  map(my_get_cor_plot)

```

Get averaged surprisals and perplexity values across all 5 random runs for each lstm model or just use first runs
```{r average}
avg_surprisals <- all_surprisals |> 
  mutate(avg_surprisal = (avg_surprisal_0+ avg_surprisal_1+ avg_surprisal_2+ avg_surprisal_3+ avg_surprisal_4)/5,
         avg_perplexity = (avg_perplexity_0+ avg_perplexity_1+ avg_perplexity_2+ avg_perplexity_3+ avg_perplexity_4)/5) |>
  select(word_clean, n_tokens, n_instances, language, avg_surprisal, avg_perplexity)

```

```{r firsts, eval=FALSE}
surprisal_path <- "./surprisals/lstm-surprisals/first_runs/"
files = list.files(path=surprisal_path, pattern="*.csv", full.names=TRUE, recursive=FALSE)
avg_surprisals <- files |> map(read_csv) |> reduce(rbind)
```

Load in surprisal results from run0 for all lang and combine them with the corresponding word lists to have all variables
```{r combine}
langs <- c("eng", "fra", "deu", "spa", "zho")
get_all_word_list <- function(lang){
  lang_path <- glue("./surprisals/word-lists/{lang}/")
  files = list.files(path=lang_path, pattern="*_clean.csv", full.names=TRUE, recursive=FALSE)
  lang_data <- files |> map(read_csv) |> reduce(rbind)
  return(lang_data)
}
word_list_data <- map(langs, get_all_word_list) |> reduce(rbind)


lstm_surprisals <- left_join(avg_surprisals, word_list_data)
saveRDS(lstm_surprisals, file ="./surprisals/lstm_surprisals.rds")

```

```{r wrangle_freq}

get_frequencies <- function(lang){
  lang_path <- glue("./surprisals/word-lists/{lang}/")
  files = list.files(path=lang_path, pattern="*_clean.csv", full.names=TRUE, recursive=FALSE)
  lang_data <- files |> map(read_csv) |> reduce(rbind)
  frequency_path <- glue("./surprisals/frequencies/{lang}_frequency_counts.csv")
  freq_data <- read_csv(frequency_path)
  combined_freq_data <- left_join(lang_data, freq_data)
  return(combined_freq_data)
}


frequencies <- map(langs, get_frequencies) |> reduce(rbind)
saveRDS(frequencies, file ="./surprisals/frequencies.rds")

```
