---
title: "childes_pipeline"
output: html_document
---

https://rpubs.com/gloukatou/736318


The get_data function extracts CHILDES corpus based on several arguments defined by the user e.g. language, date, role. 
Its output is a list of four dataframes, one with speaker information, one with utterances, one with word types and one with word tokens. 

```{r get data, echo = FALSE}
library(tidyverse)
library(childesr)
library(data.table)

#min_age, max_age, date not used yet
get_data<-function(language=NULL, 
                   corpus_name=NULL, 
                   date=NULL, 
                   collection_name=NULL, 
                   role=NULL, 
                   role_exclude=NULL, 
                   minimum_age=NULL, 
                   maximum_age=NULL, 
                   sex=NULL, 
                   educ=NULL, 
                   target_child_name=NULL, 
                   part_of_speech = NULL, 
                   stem=NULL, 
                   token=NULL){

#create speaker dataframe merging participants and statistics  
speaker_statistics<-get_speaker_statistics( collection_name, corpus_name, target_child_name, role,  role_exclude, sex)
participants<-get_participants(collection_name, corpus_name, target_child_name, role, sex)  
names(participants)[names(participants) == "id"] <- "speaker_id"
speakers<-participants %>% left_join(speaker_statistics, by=c("speaker_id", "collection_name", "collection_id", "corpus_id","target_child_id"))

#crelevant orpus_ids and speaker_ids
corpus_ids<-speakers %>% distinct(corpus_id)
speaker_ids<-speakers %>% distinct(speaker_id)

#load utterances and types
transcripts<-corpus_ids %>% left_join(get_transcripts()) 
utterances <-speaker_ids %>% left_join(get_utterances(collection_name, corpus_name, target_child_name, role, role_exclude, sex,language))
types<-speaker_ids %>% left_join(get_types(collection_name, corpus_name, target_child_name, role, role_exclude, sex,language))

#load tokens if asked
tokens<-data.frame()
if (!is.null(token)){
  tokens <-speaker_ids %>% left_join(get_tokens(token, collection_name, corpus_name, target_child_name, role, role_exclude, sex,language ))
  }

#return a list of dataframes
return(list(utterances = data.table(utterances), speakers =data.table(speakers), types =data.table(types), tokens=data.table(tokens)))
}

```

Example of get_data:

```{r call function get data}
#example
example<-get_data(collection_name="Romance")

utterances<-example$utterances
types<-example$types
speakers<-example$speakers
tokens<-example$tokens

head(utterances)
```


The wordcount function gets as input the output of get_data function. It measures word counts across levels specified by the user (by default it counts across target children, speakers, transcripts).
Its output is a list of dataframes with word counts.

```{r word count predictor}
#predictors:word_counts sent_lengths final_counts solo_counts concreteness frequency word_length valence babiness
#level on which user wants their predictor e.g. target_child_id, speaker_id, transcript_id

wordcount<-function(db,target_child_id=TRUE, speaker_id=TRUE, transcript_id=TRUE){
  
if (target_child_id==TRUE){wordcount_targetchild<- utterances %>% 
  group_by(target_child_id)  %>% 
    mutate(words = strsplit(as.character(gloss), " ")) %>% 
      unnest(words) %>% count(target_child_id, words) %>% 
        rename(wordcount = n)}

if (speaker_id==TRUE){ wordcount_speakerid<- utterances %>% 
  group_by(speaker_id)  %>% 
    mutate(words = strsplit(as.character(gloss), " ")) %>% 
      unnest(words) %>% count(speaker_id, words) %>% 
        rename(wordcount = n)  }
   
if (transcript_id==TRUE){wordcount_transcriptid<- utterances %>% 
    group_by(transcript_id)  %>% 
      mutate(words = strsplit(as.character(gloss), " ")) %>% 
        unnest(words) %>% count(transcript_id, words) %>% 
          rename(wordcount = n)  }
  
return(list(wordcount_targetchild = data.table(wordcount_targetchild), wordcount_speakerid =data.table(wordcount_speakerid), wordcount_transcriptid =data.table(wordcount_transcriptid)))

}

```

Example of wordcount function. The output of the function will be converted into a dictionary and added to the main dataframe as a column. 

```{r word count predictor example}
example2<-wordcount(utterances)

wordcount_targetchild<-example2$wordcount_targetchild
head(wordcount_targetchild)

######add to main dataframe as a dictionary????
######write.csv(tr,"/Users/lscpuser/Documents/coredata.csv" )  

```







